\chapter{The Theory of Maass Forms}
	Maass forms are the non-holomorphic analog to holomorphic forms. They are real-analytic, eigenfunctions for a differential operator, invariant with respect to a subgroup of $\PSL_{2}(\Z)$, and satisfy a growth condition. We introduce both Maass forms and their general theory.
  \section{Maass Forms}
    Define $\e(\g,z)$ by
    \[
      \e(\g,z) = \left(\frac{cz+d}{|cz+d|}\right),
    \]
    for all $\g = \begin{psmallmatrix} a & b \\ c & d \end{psmallmatrix} \in \GL_{2}^{+}(\Q)$ and $z \in \H$. Note that $|\e(\g,z)| = 1$. Moreover, we have the relation
    \[
      \e(\g,z) = \left(\frac{j(\g,z)}{|j(\g,z)|}\right).
    \]
    As a consequence, the cocycle condition for $j(\g,z)$ implies
    \[
      \e(\g'\g,z) =  \e(\g',\g z)\e(\g,z),
    \]
    and this is called the \textbf{cocycle condition}\index{cocycle condition} for $\e(\g,z)$. For any $k \in \Z$ and any $\g \in \GL_{2}^{+}(\Q)$ we define the \textbf{slash operator}\index{slash operator} $|_{\e,k}:C(\H) \to C(\H)$ to be the linear operator given by
    \[
      (f|_{\e,k}\g)(z) = \e(\g,z)^{-k}f(\g z).
    \]
    Any operator that commutes with the slash operators $|_{\e,k}\g$ for every $\g \in \PSL_{2}(\Z)$ is said to be \textbf{invariant}\index{invariant}. We define differential operators $R_{k}:C^{\infty}(\H) \to C^{\infty}(\H)$ and $L_{k}:C^{\infty}(\H) \to C^{\infty}(\H)$ to be the linear operators given by
    \[
      R_{k} = \frac{k}{2}+y\left(i\frac{\del}{\del x}+\frac{\del}{\del y}\right) \quad \text{and} \quad L_{k} = \frac{k}{2}+y\left(i\frac{\del}{\del x}-\frac{\del}{\del y}\right).
    \]
    We call these operators the \textbf{Maass differential operators}\index{Maass differential operators}. In particular, $R_{k}$ is the \textbf{Maass raising operator}\index{Maass raising operator} and $L_{k}$ is the \textbf{Mass lowering operator}\index{Maass lowering operator}. The \textbf{Laplace operator}\index{Laplace operator} $\D_{k}:C^{\infty}(\H) \to C^{\infty}(\H)$ is the linear operator given by
    \[
      \D_{k} = -y^{2}\left(\frac{\del^{2}}{\del x^{2}}+\frac{\del^{2}}{\del y^{2}}\right)+iky\frac{\del}{\del x}.
    \]
    When $k = 0$, we will write $\D_{0} = \D$ which is the usual Laplace operator on $\H$. Expanding the products $R_{k-2}L_{k}$ and $L_{k+2}R_{k}$ and invoking the Cauchy-Riemann equation
    \[
      \frac{\del}{\del y} = i\frac{\del}{\del x},
    \]
    we arrive at the identities
    \[
      \D_{k} = -R_{k-2}L_{k}+\frac{k}{2}\left(1-\frac{k}{2}\right) \quad \text{and} \quad \D_{k} = -L_{k+2}R_{k}-\frac{k}{2}\left(1-\frac{k}{2}\right).
    \]
     The Mass differential operators and the Laplace operator satisfy important relations (see \cite{bumpautomorphic1997} for a proof):

    \begin{proposition}\label{prop:Laplace_is_invariant}
      The Laplace operator $\D_{k}$ is invariant. That is,
      \[
        \D_{k}(f|_{\e,k}\g) = \D_{k}(f)|_{\e,k}\g,
      \]
      for all $f \in C^{\infty}(\H)$ and $\g \in \PSL_{2}(\Z)$. Moreover, the Maass differential operators $R_{k}$ and $L_{k}$ satisfy
      \[
        (R_{k}f)|_{\e,k+2}\g = R_{k}(f|_{\e,k}\g) \quad \text{and} \quad (R_{k}f)|_{\e,k-2}\g = L_{k}(f|_{\e,k}\g).
      \]
    \end{proposition}

    Let $\G$ be a congruence subgroup of level $N$ that is reduced at infinity and let $\chi$ be a Dirichlet character of conductor $q \mid N$. Set $\chi(\g) = \chi(d)$ for all for all $\g = \begin{psmallmatrix} a & b \\ c & d \end{psmallmatrix} \in \G$. We say that a function $f:\H \to \C$ is a \textbf{Maass form}\index{Maass form} on $\GH$ of \textbf{weight}\index{weight} $k$, \textbf{eigenvalue}\index{eigenvalue} $\l$, \textbf{level}\index{level} $N$, and \textbf{character}\index{character} $\chi$, if the following properties are satisfied:
    \begin{enumerate}[label=(\roman*)]
      \item $f$ is smooth on $\H$.
      \item $(f|_{\e,k}\g)(z) = \chi(\g)f(z)$ for all $\g \in \G$.
      \item $f$ is an eigenfunction for $\D_{k}$ with eigenvalue $\l$.
      \item $f(\a z) = o(e^{2\pi y})$ for all $\a \in \PSL_{2}(\Z)$.
    \end{enumerate}
    We say $f$ is a \textbf{(Maass) cusp form}\index{(Maass) cusp form} if the additional property is satisfied:
    \begin{enumerate}[label=(\roman*)]
      \setcounter{enumi}{4}
      \item For all cusps $\mf{a}$,
      \[
        \int_{0}^{1}f(\s_{\mf{a}}(x+iy))\,dx = 0.
      \]
    \end{enumerate}
    Property (ii) is called the \textbf{automorphy condition}\index{automorphy condition} and we say that $f$ is \textbf{automorphic}\index{automorphic}. In particular, $f$ is a function on $\mc{F}_{\G}$. The automorphy condition can equivalently be expressed as
    \[
      f(\g z) = \chi(\g)\e(\g,z)^{k}f(z).
    \]
    In property (iii), we will often let $s \in \C$ be such that $\l = s(1-s)$ and write $\l = \l(s)$ so that the eigenvalue can be determined by $s$. Property (iv) is called the \textbf{growth condition}\index{growth condition} for $f$ and we say $f$ is of \textbf{moderate growth at the cusps}\index{moderate growth at the cusps}. Clearly we only need to verify the growth condition on a set of scaling matrices for the cups. It turns turns out that Property (i) is implied by (iii). This is because $\D_{k}$ is an elliptic operator and any eigenfunction of an elliptic operator is automatically real-analytic and hence smooth (see \cite{evans2022partial} for a proof in the weight zero case and \cite{cohenmodular2017} for notes on the general case). 

    \begin{remark}\label{rem:holomorphic_embedds_into_Maass}
      Holomorphic forms embed into Maass forms. If $f(z)$ is a weight $k$ holomorphic form on $\GH$, then $F(z) = \Im(z)^{\frac{k}{2}}f(z)$ is a weight $k$ Maass form on $\GH$. This is because $\Im(\g z) = \frac{\Im(z)}{|j(\g,z)|^{2}}$ and $F(z)$ clearly has polynomial growth in $\Im(z)$. Moreover, as $f(z)$ is holomorphic, it satisfies the Cauchy-Riemann equations so that
      \[
        L_{k}(F(z)) = \left(\frac{k}{2}+y\left(i\frac{\del}{\del x}-\frac{\del}{\del y}\right)\right)(F(z)) = \frac{k}{2}F(z)-\frac{k}{2}F(z) = 0.
      \]
      Therefore
      \[
        \D_{k}(F(z)) = \left(-R_{k-2}L_{k}+\frac{k}{2}\left(1-\frac{k}{2}\right)\right)(F(z)) = \frac{k}{2}\left(1-\frac{k}{2}\right)F(z).
      \]
      This means $F(z)$ is an eigenfunction for $\D_{k}$ with eigenvalue $\l\left(\frac{k}{2}\right)$.
    \end{remark}
  
    Maass forms also admit Fourier series. Indeed, automorphy implies
    \[
      f(z+1) = f\left(\begin{pmatrix} 1 & 1 \\ 0 & 1 \end{pmatrix}z\right) = f(z),
    \]
    so that $f$ is $1$-periodic. Let $\s_{\mf{a}}$ be a scaling matrix for the $\mf{a}$ cusp. As $\G_{\mf{a}} = \s_{\mf{a}}\G_{\infty}\s_{\mf{a}}^{-1}$, or equivalently $\G_{\mf{a}}\s_{\mf{a}} = \s_{\mf{a}}\G_{\infty}$, the function $f(\s_{\mf{a}}z)$ is independent of the scaling matrix $\s_{\mf{a}}$. Moreover, by the same reasoning
    \[
      f(\s_{\mf{a}}(z+1)) = f(\s_{\mf{a}}z).
    \]
    Thus $f(\s_{\mf{a}}z)$ is $1$-periodic. Note that this means we only need to verify the growth condition as $y \to \infty$. As $f$ is smooth, $f(\s_{\mf{a}}z)$ has a Fourier series
    \[
      f(\s_{\mf{a}}z) = \sum_{n \in \Z}a_{\mf{a}}(n,y)e^{2\pi inx},
    \]
    where the sum is over all $n \in \Z$ since $f$ may be unbounded. This Fourier series is independent of the scaling matrix because $f(\s_{\mf{a}}z)$ is. The Fourier coefficients $a_{\mf{a}}(n,y)$ are mostly determined by $\D_{k}$. To see this, since $f$ is smooth we may differentiate the Fourier series of $f(\s_{\mf{a}}z)$ termwise. The fact that $f$ is an eigenfunction for $\D_{k}$ with eigenvalue $\l$ gives the ODE
    \[
      (4\pi^{2}n^{2}y^{2}-2\pi nky)a_{\mf{a}}(n,y)-y^{2}a_{\mf{a},yy}(n,y) = \l a_{\mf{a}}(n,y).
    \]
    If $n \neq 0$, this is a Whittaker equation. To see this, first put the ODE in homogeneous form
    \[
      y^{2}a_{\mf{a},yy}(n,y)-(4\pi^{2}n^{2}y^{2}-2\pi nky-\l)a_{\mf{a}}(n,y) = 0.
    \]
    Now make the change of variables $y \to \frac{y}{4\pi|n|}$ to get
    \[
      y^{2}a_{\mf{a},yy}(n,4\pi|n|y)-\left(\frac{y^{2}}{4}-\sgn(n)\frac{k}{2}y-\l\right)a_{\mf{a}}(n,4\pi|n|y) = 0,
    \]
    where $\sgn(n) = \pm1$ if $n$ is positive or negative respectively. Diving by $y^{2}$ results in
    \[
      a_{\mf{a},yy}(n,4\pi|n|y)+\left(\frac{1}{4}-\frac{\sgn(n)\frac{k}{2}}{y}-\frac{\l}{y^{2}}\right)a_{\mf{a}}(n,4\pi|n|y) = 0.
    \]
    Upon writing $\l = s(1-s)$, we see that $\l = \frac{1}{4}-(s-\frac{1}{2})^{2}$, and the above equation becomes
    \[
      a_{\mf{a},yy}(n,4\pi|n|y)+\left(\frac{1}{4}-\frac{\sgn(n)\frac{k}{2}}{y}-\frac{\frac{1}{4}-\left(s-\frac{1}{2}\right)^{2}}{y^{2}}\right)a_{\mf{a}}(n,4\pi|n|y) = 0.
    \]
    This is the Whittaker equation (see \cref{append:Whittaker_Functions}). Since $f$ has moderate growth at the cusps, the general solution is the Whittaker function $W_{\sgn(n)\frac{k}{2},s-\frac{1}{2}}(4\pi|n|y)$. Therefore
    \[
      a_{\mf{a}}(n,y) = a_{\mf{a}}(n)W_{\sgn(n)\frac{k}{2},s-\frac{1}{2}}(4\pi|n|y),
    \]
    for some coefficients $a_{\mf{a}}(n)$ and $b_{\mf{a}}(n)$ possibly depending upon $s$. If $n = 0$, then the differential equation is a second order linear ODE which in is
    \[
      -y^{2}a_{\mf{a},yy}(0,y) = \l a_{\mf{a}}(0,y).
    \]
    This is a Cauchy-Euler equation, and since $s$ and $1-s$ are the two roots of $z^{2}-z+\l$, the general solution is
    \[
      a_{\mf{a}}(0,y) = a_{\mf{a}}(0)y^{s}+b_{\mf{a}}(0)y^{1-s},
    \]
    for some coefficients $a_{\mf{a}}(0)$ and $b_{\mf{a}}(0)$ possibly depending upon $s$. The coefficients $a_{\mf{a}}(n)$, $a_{\mf{a}}(0)$, and $b_{\mf{a}}(0)$ are the only part of the Fourier series that actually depend on the implicit congruence subgroup $\G$. Using these coefficients, $f$ admits a \textbf{Fourier series at the $\mf{a}$ cusp}\index{Fourier series at the $\mf{a}$ cusp}:
    \[
      f(\s_{\mf{a}}z) = a_{\mf{a}}(0)y^{s}+b_{\mf{a}}(0)y^{1-s}+\sum_{n \neq 0}a_{\mf{a}}(n)W_{\sgn(n)\frac{k}{2},s-\frac{1}{2}}(4\pi|n|y)e^{2\pi inx}.
    \]
    For ease of notation, if it is clear what cusp we are working at we will mention the Fourier series and its coefficients without mentioning the cusp. Moreover, property (v) implies that $f$ is a cusp form if and only if $a_{\mf{a}}(0) = 0$ and $b_{\mf{a}}(0) = 0$ for every cusp $\mf{a}$. We can simplify this Fourier series in the weight zero case. Indeed, \cref{thm:Whittaker_special_cases} implies that the Fourier series at the $\mf{a}$ cusp takes the form
    \[
      f(\s_{\mf{a}}z) = a_{\mf{a}}(0)y^{s}+b_{\mf{a}}(0)y^{1-s}+\sum_{n \neq 0}a_{\mf{a}}(n)\sqrt{y}K_{s-\frac{1}{2}}(2\pi|n|y)e^{2\pi inx},
    \]
    for some different Fourier coefficients $a_{\mf{a}}(n)$. We can simplify the Fourier series further. We say $f$ is \textbf{even}\index{even} if $f(-\conj{z}) = f(z)$ and is \textbf{odd}\index{odd} if $f(-\conj{z}) = -f(z)$. Since $-\conj{z} = -x+iy$, this means that $f$ is even or odd with respect to $x$. Note that if $f$ is odd it must be a cusp form. As $e^{2\pi inx} = \cos(nx)+i\sin(nx)$, if $f$ has eigenvalue $\l = s(1-s)$, then the Fourier series of $f$ at the $\mf{a}$ cusp takes the form
    \[
      f(\s_{\mf{a}}z) = a_{\mf{a}}(0)y^{s}+b_{\mf{a}}(0)y^{1-s}+\sum_{n \neq 0}a_{\mf{a}}(n)\sqrt{y}K_{s-\frac{1}{2}}(2\pi|n|y)\cos\left(\frac{2\pi nx}{t}\right),
    \]
    if $f$ is even, and
    \[
      f(z) = \sum_{n \neq 0}a_{\mf{a}}(n)i\sqrt{y}K_{s-\frac{1}{2}}(2\pi|n|y)\sin\left(\frac{2\pi nx}{t}\right),
    \]
    if $f$ is odd. Therefore, in even case $a_{\mf{a}}(-n) = a_{\mf{a}}(n)$ and in the odd case $-a_{\mf{a}}(-n) = a_{\mf{a}}(n)$ for all $n \ge 1$. Either way, we can compactly write the Fourier series of $f$ at the $\mf{a}$ cusp as
    \[
      f(\s_{\mf{a}}z) = a_{\mf{a}}(0)y^{s}+b_{\mf{a}}(0)y^{1-s}+\sum_{n \ge 1}a_{\mf{a}}(n)\sqrt{y}K_{s-\frac{1}{2}}(2\pi ny)\SC\left(\frac{2\pi nx}{t}\right),
    \]
    for some different Fourier coefficients $a_{\mf{a}}(n)$ and where $\SC(x) = \cos(x)$ if $f$ is even and $\SC(x) = \sin(x)$ if $f$ is odd. As we have said, if $f$ is odd, or more generally a cusp form, then necessarily $a_{\mf{a}}(0) = 0$ and $b_{\mf{a}}(0) = 0$. From now on, if we are discussing an even or odd Maass form we will always mean the corresponding Fourier series (and so the implicit weight is zero). For cusp forms, we can derive an important growth condition. Indeed, the Fourier series of $f$ at the $\mf{a}$ cusp is given by
    \[
      f(\s_{\mf{a}}z) = \sum_{n \neq 0}a_{\mf{a}}(n)W_{\sgn(n)\frac{k}{2},s-\frac{1}{2}}(4\pi|n|y)e^{2\pi inx}.
    \]
    Using \cref{lem:Whittaker_function_asymptotic}, we get the weaker asymptotic $W_{\sgn(n)\frac{k}{2},s-\frac{1}{2}}(4\pi|n|y) = O(y^{\frac{k}{2}}e^{-2\pi|n|y})$ which implies
    \[
      f(\s_{\mf{a}}z) = O\left(y^{\frac{k}{2}}\sum_{n \neq 0}e^{-2\pi|n|y}\right) = O\left(y^{\frac{k}{2}}\sum_{n \in \Z}e^{-2\pi|n|y}\right) = O\left(\frac{2y^{\frac{k}{2}}}{1-e^{-2\pi y}}\right) = O(y^{\frac{k}{2}}e^{-2\pi y}).
    \]
    Accordingly, we say that $f$ exhibits \textbf{moderate decay at the cusps}\index{moderate decay at the cusps}. In particular, $f$ is bounded on $\H$.
  \section{Eisenstein \& Poincar\'e Series}
    Throughout, let $\G$ be a congruence subgroup of level $N$ and let $\chi$ be a Dirichlet character with conductor $q \mid N$. We will first introduce a class of Maass forms naturally defined on $\GH$. They are actually functions defined on a large space $\H \x \C$ and hence are functions of two variables namely $z$ and $s$. These functions are Maass forms for fixed $s$. For every cusp $\mf{a}$ of $\GH$, there is an associated Maass form. So let $\s_{\mf{a}}$ be a scaling matrix for the cusp $\mf{a}$. The \textbf{(Maass) Eisenstein series}\index{(Maass) Eisenstein series} $E_{k,\chi,\mf{a}}(z,s)$ of weight $k$ and character $\chi$ on $\GH$ at the $\mf{a}$ cusp and is defined as
    \[
      E_{k,\chi,\mf{a}}(z,s) = \sum_{\g \in \G_{\mf{a}}\backslash\G}\cchi(\g)\e(\s_{\mf{a}}^{-1}\g,z)^{-k}\Im(\s_{\mf{a}}^{-1}\g z)^{s}.
    \]
    We first show that $E_{k,\chi,\mf{a}}(z,s)$ is well-defined. To see that $\cchi(\g)$ is independent of $\g$, recall $\G_{\mf{a}} = \s_{\mf{a}}\G_{\infty}\s_{\mf{a}}^{-1}$ and let $\g' = \s_{\mf{a}}\eta_{\infty}\s_{\mf{a}}^{-1}\g$ with $\eta_{\infty} = \begin{psmallmatrix} 1 & n \\ 0 & 1 \end{psmallmatrix} \in \G_{\infty}$. Then
    \[
      \chi(\g') = \chi(\s_{\mf{a}}\eta_{\infty}\s_{\mf{a}}^{-1}\g) = \chi(\s_{\mf{a}})\chi(\eta_{\infty})\chi(\s_{\mf{a}})^{-1}\chi(\g) = \chi(\g).
    \]
    This verifies that $\cchi(\g)$ is independent of the representative $\g$. Moreover, we can write $\g' = \eta_{\mf{a}}\g$ where $\eta_{\mf{a}} = \s_{\mf{a}}\eta_{\infty}\s_{\mf{a}}^{-1}$ and so $\s_{\mf{a}}^{-1}\g' = (\s_{\mf{a}}')^{-1}\g$ for some other scaling matrix $\s_{\mf{a}}' = \eta_{\mf{a}}^{-1}\s_{\mf{a}}$. Therefore we are left to verify that $E_{k,\chi,\mf{a}}(z,s)$ is independent of the scaling matrix $\s_{\mf{a}}$. Writing $(\s_{\mf{a}}')^{-1} = \eta_{\infty}\s_{\mf{a}}^{-1}$ and noting that $\eta_{\infty}$ does not affect the imaginary part as it acts by translation, we conclude $\Im((\s_{\mf{a}}')^{-1}\g z) = \Im(\s_{\mf{a}}^{-1}\g z)$. Therefore $\Im(\s_{\mf{a}}^{-1}\g z)$ in independent of the scaling matrix used. Similarly, the cocycle relation implies
    \[
      \e((\s_{\mf{a}}')^{-1}\g,z) = \e(\eta_{\infty}\s_{\mf{a}}^{-1}\g,z) = \e(\eta_{\infty},\s_{\mf{a}}^{-1}\g z)\e(\s_{\mf{a}}^{-1}\g,z) = \e(\s_{\mf{a}}^{-1}\g,z),
    \]
    where the last equality follows because $\e(\eta_{\infty},\s_{\mf{a}}^{-1}\g z) = 1$ (as $j(\eta_{\infty},\s_{\mf{a}}^{-1}\g z) = 1$). Thus $\e(\s_{\mf{a}}^{-1}\g,z)$ is also independent of the scaling matrix used. Altogether, this shows $E_{k,\chi,\mf{a}}(z,s)$ is independent of the scaling matrix used and thus is well-defined. We now show that this series is locally absolutely uniformly convergent for $z \in \H$ and $\Re(s) > 1$. To see this, applying the Bruhat decomposition to $\s_{\mf{a}}^{-1}\G_{\mf{a}}\backslash\G = \G_{\infty}\backslash\s_{\mf{a}}^{-1}\G$ yields
    \[
      E_{k,\chi,\mf{a}}(z,s) \ll \sum_{(c,d) \in \Z^{2}-\{\mathbf{0}\}}\frac{\Im(z)^{\s}}{|cz+d|^{2\s}}.
    \]
    The latter series is locally absolutely uniformly convergent for $\s > 1$ and $z \in \H$ by \cref{prop:general_lattice_sum_convergence_for_two_variables}. Therefore $E_{k,\chi,\mf{a}}(z,s)$ does too. To see that it is automorphic on $\GH$, let $\g \in \G$. Then we make a short computation:
    \begin{align*}
      E_{k,\chi,\mf{a}}(\g z,s) &= \sum_{\g' \in \G_{\mf{a}}\backslash\G}\cchi(\g')\e(\s_{\mf{a}}^{-1}\g',\g z)^{-k}\Im(\s_{\mf{a}}^{-1}\g'\g z)^{s} \\
      &= \sum_{\g' \in \G_{\mf{a}}\backslash\G}\cchi(\g')\left(\frac{\e(\s_{\mf{a}}^{-1}\g'\g,z)}{\e(\g,z)}\right)^{-k}\Im(\s_{\mf{a}}^{-1}\g'\g z)^{s} && \text{cocycle condition} \\
      &= \e(\g,z)^{k}\sum_{\g' \in \G_{\mf{a}}\backslash\G}\cchi(\g')\e(\s_{\mf{a}}^{-1}\g'\g,z)^{-k}\Im(\s_{\mf{a}}^{-1}\g'\g z)^{s} \\
      &= \chi(\g)\e(\g,z)^{k}\sum_{\g' \in \G_{\mf{a}}\backslash\G}\cchi(\g')\cchi(\g)\e(\s_{\mf{a}}^{-1}\g'\g,z)^{-k}\Im(\s_{\mf{a}}^{-1}\g'\g z)^{s} \\
      &= \chi(\g)\e(\g,z)^{k}\sum_{\g' \in \G_{\mf{a}}\backslash\G}\cchi(\g'\g)\e(\s_{\mf{a}}^{-1}\g'\g,z)^{-k}\Im(\s_{\mf{a}}^{-1}\g'\g z)^{s} \\
      &= \chi(\g)\e(\g,z)^{k}\sum_{\g' \in \G_{\mf{a}}\backslash\G}\cchi(\g')\e(\s_{\mf{a}}^{-1}\g',z)^{-k}\Im(\s_{\mf{a}}^{-1}\g' z)^{s} && \text{$\g' \to \g'\g^{-1}$ bijection on $\G$} \\
      &= \chi(\g)\e(\g,z)^{k}E_{k,\chi,\mf{a}}(z,s).
    \end{align*}
    Now we show that it is an eigenfunction for $\D_{k}$. Observe that
    \[
      \D_{k}(y^{s}) = \left(-y^{2}\left(\frac{\del^{2}}{\del x^{2}}+\frac{\del^{2}}{\del y^{2}}\right)+iky\frac{\del}{\del x}\right)(y^{s}) = \l(s)y^{s}.
    \]
    Therefore $\Im(z)^{s}$ is an eigenfunction for $\D_{k}$ with eigenvalue $\l(s)$. Since $\D_{k}$ is invariant,
    \[
      \D_{k}((\Im(\cdot)^{s}|_{\e,k}\g)(z)) = ((\D_{k}\Im(\cdot)^{s})|_{\e,k}\g)(z) = \l(s)(\Im(\cdot)^{s}|_{\e,k}\g)(z),
    \]
    and so $(\Im(\cdot)^{s}|_{\e,k}\g)(z) = \e(\g,z)^{-k}\Im(\g z)^{s}$ is also an eigenfunction for $\D_{k}$ with eigenvalue $\l(s)$ for all $\g \in \PSL_{2}(\Z)$. We immediately conclude that
    \[
      \D_{k}(E_{k,\chi,\mf{a}}(z,s)) = \l(s)E_{k,\chi,\mf{a}}(z,s),
    \]
    which shows $E_{k,\chi,\mf{a}}(z,s)$ is also an eigenfunction for $\D_{k}$ with eigenvalue $\l(s)$. We now verify the growth condition for $E_{k,\chi,\mf{a}}(z,s)$. Let $\s_{\mf{b}}$ be a scaling matrix for the cusp $\mf{b}$ and write $\s_{\mf{b}} = \begin{psmallmatrix} a' & b' \\ c' & d' \end{psmallmatrix}$. Then
    \[
      E_{k,\chi,\mf{a}}(\s_{\mf{b}}z,s) \ll \sum_{(c,d) \in \Z^{2}-\{\mathbf{0}\}}\frac{\Im(\s_{\mf{b}}z)^{\s}}{|c\s_{\mf{b}}z+d|^{2\s}} = \frac{\Im(z)^{\s}}{|c'z+d'|^{2\s}}\sum_{(c,d) \in \Z^{2}-\{\mathbf{0}\}}\frac{1}{|c\s_{\mf{b}}z+d|^{2\s}}.
    \]
    Now decompose this last sum as
    \[
      \sum_{(c,d) \in \Z^{2}-\{\mathbf{0}\}}\frac{1}{|c\s_{\mf{b}}z+d|^{2\s}} = \sum_{d \neq 0}\frac{1}{d^{2\s}}+\sum_{c \neq 0}\sum_{d \in \Z}\frac{1}{|c\s_{\mf{b}}z+d|^{2\s}} = 2\sum_{d \ge 1}\frac{1}{d^{2\s}}+2\sum_{c \ge 1}\sum_{d \in \Z}\frac{1}{|c\s_{\mf{b}}z+d|^{2\s}}.
    \]
    Notice that $\sum_{c \ge 1}\sum_{d \in \Z}\frac{1}{d^{2\s}}$ converges provided $\s > 1$. Moreover, the exact same argument as for holomorphic form Eisenstein series shows that $\sum_{c \ge 1}\sum_{d \in \Z}\frac{1}{|c\s_{\mf{b}}z+d|^{2s}}$ converges in this region as well. Now for all $\Im(z) \ge 1$ and $\s > 1$,
    \[
      \frac{\Im(z)^{\s}}{|c'z+d'|^{2\s}} \ll \frac{\Im(z)^{\s}}{|c'\Im(z)|^{2\s}} \ll \Im(z)^{\s}.
    \]
    So altogether,
    \[
      E_{\mf{a}}(\s_{\mf{b}}z,s) \ll \Im(z)^{\s} = o(e^{2\pi\Im(z)}),
    \]
    provided $\Im(z) \ge 1$ and $\s > 1$. This verifies $E_{k,\chi,\mf{a}}(z,s)$ is of moderate growth at the cusps. We collect all of this work as a theorem:

    \begin{theorem}
      For $\Re(s) > 1$, the Eisenstein series
      \[
          E_{k,\chi,\mf{a}}(z,s) = \sum_{\g \in \G_{\mf{a}}\backslash\G}\cchi(\g)\e(\s_{\mf{a}}^{-1}\g,z)^{-k}\Im(\s_{\mf{a}}^{-1}\g z)^{s},
      \]
      is a weight $k$ Maass form with eigenvalue $\l(s)$ and character $\chi$ on $\GH$.
    \end{theorem}

    It is now time to discuss the Poincar\'e series. Unlike in the holomorphic case, the Poincar\'e series are not genuine Maass forms. However, they are still automorphic functions. Let $\psi(y)$ be a smooth function such that $\psi(y) \ll_{\e} y^{1+\e}$ as $y \to 0$. Let $\s_{\mf{a}}$ be a scaling matrix for the $\mf{a}$ cusp and let $m \ge 1$. Then the $m$-th \textbf{(automorphic) Poincar\'e series}\index{(automorphic) Poincar\'e series} $P_{m,k,\chi,\mf{a}}(z,\psi)$ of weight $k$ and character $\chi$ on $\GH$ at the $\mf{a}$ cusp and with respect to $\psi(y)$ is defined by
    \[
      P_{m,k,\chi,\mf{a},m}(z,\psi) = \sum_{\g \in \G_{\mf{a}}\backslash\G}\cchi(\g)\e(\s_{\mf{a}}^{-1}\g,z)^{-k}\psi(\Im(\s_{\mf{a}}^{-1}\g z))e^{2\pi im\s_{\mf{a}}^{-1}\g z}.
    \]
    We first show $P_{m,k,\chi,\mf{a}}(z,\psi)$ is well-defined. We have already showed that $\cchi(\g)$ is independent of the representative $\g$ and $\e(\s_{\mf{a}}^{-1}\g,z)^{-k}$ and $\Im(\s_{\mf{a}}^{-1}\g z)$ are independent of the scaling matrix used when discussing $E_{k,\chi,\mf{a}}(z,s)$. So it suffices to show that $e^{2\pi im\s_{\mf{a}}^{-1}\g z}$ is independent of the scaling matrix too. As before, suppose $\s_{\mf{a}}' = \eta_{\mf{a}}^{-1}\s_{\mf{a}}$ with $\eta_{\mf{a}} = \s_{\mf{a}}\eta_{\infty}\s_{\mf{a}}^{-1}$ and $\eta_{\infty} = \begin{psmallmatrix} 1 & n \\ 0 & 1 \end{psmallmatrix} \in \G_{\infty}$. Then $(\s_{\mf{a}}')^{-1} = \eta_{\infty}\s_{\mf{a}}^{-1}$, and we have
    \[
      e^{2\pi im(\s_{\mf{a}}')^{-1}\g z} = e^{2\pi im\eta_{\infty}\s_{\mf{a}}^{-1}\g z} = e^{2\pi im(\s_{\mf{a}}^{-1}\g z+n)} = e^{2\pi im\s_{\mf{a}}^{-1}\g}e^{2\pi imnz} = e^{2\pi im\s_{\mf{a}}^{-1}\g},
    \]
    and hence $e^{2\pi im\s_{\mf{a}}^{-1}\g z}$ is independent of the representative $\g$ used. It follows that $P_{m,k,\chi,\mf{a}}(z,\psi)$ is well-defined. Moreover, $P_{m,k,\chi,\mf{a}}(z,\psi)$ is locally absolutely uniformly convergent for $z \in \H$, but to see this we first require a technical lemma:

    \begin{lemma}\label{lem:finitely_many_pairs_with_size_larger_than_one}
      For any compact subset $K$ of $\H$, there are finitely many pairs $(c,d) \in \Z^{2}-\{\mathbf{0}\}$, with $c \neq 0$, for which
      \[
        \frac{\Im(z)}{|cz+d|^{2}} > 1,
      \]
      for all $z \in K$.
      \end{lemma}
      \begin{proof}
      Let $\b = \sup_{z \in K}|z|$ . As $|cz+d| \ge |cz| > 0$ and $\Im(z) < |z|$, we have
      \[
        \frac{\Im(z)}{|cz+d|^{2}} \le \frac{1}{|c|^{2}|z|} \le \frac{1}{|c|^{2}\b}.
      \]
      So if $\frac{\Im(z)}{|cz+d|^{2}} > 1$, then $\frac{1}{|c|^{2}\b} > 1$ which is to say $|c| < \frac{1}{\sqrt{\b}}$ and therefore $|c|$ is bounded. On the other hand, $|cz+d| \ge |d| \ge 0$. Excluding the finitely many terms $(c,0)$, we may assume $|d| > 0$. In this case, similarly  
      \[
        \frac{\Im(z)}{|cz+d|^{2}} \le \frac{|z|}{|d|^{2}} \le \frac{\b}{|d|^{2}}.
      \]
      So if $\frac{\Im(z)}{|cz+d|^{2}} > 1$, then $\frac{\b}{|d|^{2}}> 1$ which is to say $|d| < \sqrt{\b}$. So $|d|$ is also bounded. Since both $|c|$ and $|d|$ are bounded, the claim follows.
    \end{proof}
    
    Now we are ready to show that $P_{m,k,\chi,\mf{a}}(z,\psi)$ is locally absolutely uniformly convergent. Let $K$ be a compact subset of $\H$. Then it suffices to show $P_{m,k,\chi,\mf{a}}(z,\psi)$ is uniformly convergent on $K$. Applying the Bruhat decomposition to $\s_{\mf{a}}^{-1}\G_{\mf{a}}\backslash\G = \G_{\infty}\backslash\s_{\mf{a}}^{-1}\G$ gives
    \[
      P_{m,k,\chi,\mf{a}}(z,\psi) \ll |\psi(\Im(z))|+\sum_{\substack{(c,d) \in \Z^{2}-\{\mathbf{0}\}}}\left|\psi\left(\frac{\Im(z)}{|cz+d|^{2}}\right)\right|.
    \]
    It now further suffices to show that the series above is uniformly convergent on $K$. By \cref{lem:finitely_many_pairs_with_size_larger_than_one} there are all but finitely many terms in the sum with $\psi\left(\frac{\Im(z)}{|cz+d|^{2}}\right) \ll \left(\frac{\Im(z)}{|cz+d|^{2}}\right)^{1+\e}$. But the finitely many other terms are all uniformly bounded on $K$ because $\psi(y)$ is continuous (as it is smooth). Therefore
    \[
      \sum_{(c,d) \in \Z^{2}-\{\mathbf{0}\}}\left|\psi\left(\frac{\Im(z)}{|cz+d|^{2}}\right)\right| \ll_{\e} \sum_{(c,d) \in \Z^{2}-\{\mathbf{0}\}}\left(\frac{\Im(z)}{|cz+d|^{2}}\right)^{1+\e},
    \]
    and this last series is locally absolutely uniformly convergent for $z \in \H$ by \cref{prop:general_lattice_sum_convergence_for_two_variables}. It follows that $P_{m,k,\chi,\mf{a}}(z,\psi)$ is too. Automorphy for $P_{m,k,\chi,\mf{a}}(z,\psi)$ is verified in exactly the same way as for $E_{k,\chi,\mf{a}}(z,s)$. We collect this work as a theorem:

    \begin{theorem}
      Let $\psi(y)$ be a smooth function such that $\psi(y) \ll_{\e} y^{1+\e}$ as $y \to 0$. The Poincar\'e series
      \[
        P_{m,k,\chi,\mf{a}}(z,\psi) = \sum_{\g \in \G_{\mf{a}}\backslash\G}\cchi(\g)\e(\s_{\mf{a}}^{-1}\g,z)^{-k}\psi(\Im(\s_{\mf{a}}^{-1}\g z))e^{2\pi im\s_{\mf{a}}^{-1}\g z},
      \]
      is a holomorphic automorphic function on $\GH$.
    \end{theorem}
  \section{\texorpdfstring{$L^{2}$}{L{2}}-integrable Automorphic Functions}
    We will describe the space of automorphic functions and appropriate subspaces of interest. Let $\G$ be a congruence subgroup of level $N$ and let $\chi$ be a Dirichlet character of conductor $q \mid N$. We will let $\mc{A}_{k}(\G,\chi)$ denote the space of all automorphic functions of weight $k$ and character $\chi$ on $\GH$. Let $\mc{L}_{k}(\G,\chi)$ be the subspace of $\mc{A}_{k}(\G,\chi)$ consisting of those functions with bounded norm where the norm is given by
    \[
      ||f|| = \left(\frac{1}{V_{\G}}\int_{\mc{F}_{\G}}|f(z)|^{2}\,d\mu\right)^{\frac{1}{2}}.
    \]
    Moreover, if $\chi$ is the trivial character of if $k = 0$, we will suppress the dependences accordingly. Since $f$ is automorphic, the integral $\G$-invariant and hence is independent of the choice of fundamental domain. Since this is an $L^{2}$-space, $\mc{L}_{k}(\G,\chi)$ is an induced inner product space (because the parallelogram law is satisfied). In particular, for any $f,g \in \mc{L}_{k}(\G,\chi)$ we define their \textbf{Petersson inner product}\index{Petersson inner product} to be
    \[
      \<f,g\>_{\G} = \frac{1}{V_{\G}}\int_{\mc{F}_{\G}}f(z)\conj{g(z)}\,d\mu.
    \]
    If the congruence subgroup is clear from context we will suppress the dependence upon $\G$. The integral is locally absolutely uniformly bounded by the Cauchy–Schwarz inequality and that $f,g \in \mc{L}_{k}(\G,\chi)$. As $f$ and $g$ are automorphic, the integral is independent of the choice of fundamental domain. These two facts imply that the Petersson inner product is well-defined. We will continue to use this notion even if $f$ and $g$ do not belong to $\mc{L}_{k}(\G,\chi)$ provided the integral is locally absolutely uniformly bounded. Moreover, we have the following proposition:

    \begin{proposition}
      $\mc{L}_{k}(\G,\chi)$ is a Hilbert space with respect to the Petersson inner product.
    \end{proposition}
    \begin{proof}
      To show that the Petersson inner product is a Hermitian inner product on $\mc{L}_{k}(\G,\chi)$, just mimic the corresponding part of proof of \cref{prop:Petersson_inner_product_hermitian} with $k = 0$. We now show that $\mc{L}_{k}(\G,\chi)$ is complete. Let $(f_{n})_{n \ge 1}$ be a Cauchy sequence in $\mc{L}_{k}(\G,\chi)$. Then $||f_{n}-f_{m}|| \to 0$ as $n,m \to \infty$. But
      \[
        ||f_{n}-f_{m}|| = \left(\frac{1}{V_{\G}}\int_{\mc{F}_{\G}}|f_{n}(z)-f_{m}(z)|^{2}\,d\mu\right)^{\frac{1}{2}},
      \]
      and this integral tends to zero if and only if $|f_{n}(z)-f_{m}(z)| \to 0$ as $n,m \to \infty$. Therefore $\lim_{n \to \infty}f_{n}(z)$ exists and we define the limiting function $f$ by $f(z) = \lim_{n \to \infty}f_{n}(z)$. We claim that $f$ is automorphic. Indeed, as the $f_{n}$ are automorphic, we have
      \[
        f(\g z) = \lim_{n \to \infty}f_{n}(\g z) = \lim_{n \to \infty}\chi(\g)\e(\g,z)^{k}f_{n}(z) = \chi(\g)\e(\g,z)^{k}\lim_{n \to \infty}f_{n}(z) = \chi(\g)\e(\g,z)^{k}f(z),
      \]
      for any $\g \in \G$. Also, $||f|| < \infty$. To see this, since $(f_{n})_{n \ge 1}$ is Cauchy we know $(||f_{n}||)_{n \ge 1}$ converges. In particular, $\lim_{n \to \infty}||f_{n}|| < \infty$. But
      \[
        \lim_{n \to \infty}||f_{n}|| = \lim_{n \to \infty}\left(\frac{1}{V_{\G}}\int_{\mc{F}_{\G}}|f_{n}(z)|^{2}\,d\mu\right)^{\frac{1}{2}} = \left(\frac{1}{V_{\G}}\int_{\mc{F}_{\G}}\left|\lim_{n \to \infty}f_{n}(z)\right|^{2}\,d\mu\right)^{\frac{1}{2}} = \left(\frac{1}{V_{\G}}\int_{\mc{F}_{\G}}|f(z)|^{2}\,d\mu\right)^{\frac{1}{2}} = ||f||,
      \]
      where the second equality holds by the dominated convergence theorem. Hence $||f|| < \infty$ as desired and so $f \in \mc{L}_{k}(\G,\chi)$. We now show that $f_{n} \to f$ in the $L^{2}$-norm. Indeed,
      \[
        ||f(z)-f_{n}(z)|| = \left(\frac{1}{V_{\G}}\int_{\mc{F}_{\G}}|f(z)-f_{n}(z)|^{2}\,d\mu\right)^{\frac{1}{2}},
      \]
      and it follows that $||f(z)-f_{n}(z)|| \to 0$ as $n \to \infty$ so that the Cauchy sequence $(f_{n})_{n \ge 1}$ converges.
    \end{proof}

    We will need two more subspaces. Let $\mc{B}_{k}(\G,\chi)$ be the subspace of $\mc{A}_{k}(\G,\chi)$ such that $f$ is smooth and bounded and let $\mc{D}_{k}(\G,\chi)$ be the subspace of $\mc{A}_{k}(\G,\chi)$ such that $f$ and $\D_{k}f$ are smooth and bounded. Again, if $\chi$ is the trivial character of if $k = 0$, we will suppress the dependences accordingly. Since boundedness on $\H$ implies square-integrability over $\mc{F}_{\G}$, we have the following chain of inclusions:
    \[
      \mc{D}_{k}(\G,\chi) \subseteq \mc{B}_{k}(\G,\chi) \subseteq \mc{L}_{k}(\G,\chi) \subseteq \mc{A}_{k}(\G,\chi).
    \]
    Moreover, $\mc{D}_{k}(\G,\chi)$ is almost all of $\mc{L}_{k}(\G,\chi)$ as the following proposition shows:

    \begin{proposition}\label{prop:dense_subspace_of_square-integrable_modular_functions}
      $\mc{D}_{k}(\G,\chi)$ is dense in $\mc{L}_{k}(\G,\chi)$.
    \end{proposition}
    \begin{proof}
      Note that $\mc{D}_{k}(\G,\chi)$ is an algebra of functions that vanish at infinity. We will show that $\mc{D}_{k}(\G,\chi)$ is nowhere vanishing, separates points, and is self-adjoint. For nowhere vanishing fix a $z \in \H$. Let $\vphi_{z}$ be a bump function defined on some sufficiently small neighborhood $U_{z}$ of $z$. Then
      \[
        \Phi(v) = \sum_{\g \in \G_{\infty}\backslash\G}\cchi(\g)\e(\g,v)^{-k}\vphi_{z}(\g v),
      \]
      belongs to $\mc{D}_{k}(\G,\chi)$ and is nonzero at $z$ (the automorphy follows exactly as in the case of Eisenstein series). We now show $\mc{D}_{k}(\G,\chi)$ also separates points. To see this consider two distinct points $z,w \in \H$. Let $U_{z,w}$ be a small neighborhood of $z$ not containing $w$. Then $\Phi_{z}\mid_{U_{z,w}}$ belongs to $\mc{D}_{k}(\G,\chi)$ with $\Phi_{z}\mid_{U_{z,w}}(z) \neq 0$ and $\vphi_{z}\mid_{U_{z,w}}(w) = 0$. To see why $\mc{D}_{k}(\G,\chi)$ is self-adjoint, recall that complex conjugation is smooth and commutes with partial derivatives so that if $f$ belongs to $\mc{D}_{k}(\G,\chi)$ then so does $\conj{f}$. Therefore the Stone–Weierstrass theorem for complex functions defined on locally compact Hausdorff spaces (as $\H$ is a locally compact Hausdorff space) implies that $\mc{D}_{k}(\G,\chi)$ is dense in $C_{0}(\H)$ with the supremum norm. Note that $\mc{L}_{k}(\G,\chi) \subseteq C_{0}(\H)$ on the level of sets. Now we show $\mc{D}_{k}(\G,\chi)$ is dense in $\mc{L}_{k}(\G,\chi)$. Let $f \in \mc{L}_{k}(\G,\chi)$. By what we have just show, there exists a sequence $(f_{n})_{n \ge 1}$ in $\mc{D}_{k}(\G,\chi)$ converging to $f$ in the supremum norm. But 
      \[
        ||f-f_{n}|| = \left(\frac{1}{V_{\G}}\int_{\mc{F}_{\G}}|f(z)-f_{n}(z)|^{2}\,d\mu\right)^{\frac{1}{2}} \le \left(\frac{1}{V_{\G}}\int_{\mc{F}_{\G}}\sup_{z \in \mc{F}_{\G}}|f(z)-f_{n}(z)|^{2}\,d\mu\right)^{\frac{1}{2}},
      \]
      and the last expression tends to zero as $n \to \infty$ because $f_{n} \to f$ in the supremum norm.
    \end{proof}

    As $\mc{D}_{k}(\G,\chi) \subseteq \mc{B}_{k}(\G,\chi)$, \cref{prop:dense_subspace_of_square-integrable_modular_functions} implies that $\mc{B}_{k}(\G,\chi)$ is dense in $\mc{L}_{k}(\G,\chi)$ too. It can be shown that the Laplace operator $\D_{k}$ is positive and symmetric on $\mc{D}_{k}(\G,\chi)$ and hence admits a self-adjoint extension to $\mc{L}_{k}(\G,\chi)$ (see \cite{iwaniec2002spectral} for a proof in the weight zero case and \cite{cohenmodular2017} for notes on the general case):

    \begin{theorem}\label{thm:Laplace_semi-definite_self-adjoint}
      On $\mc{L}_{k}(\G,\chi)$, the Laplace operator $\D_{k}$ is positive semi-definite and self-adjoint.
    \end{theorem}

    If we suppose $f \in \mc{L}_{k}(\G,\chi)$ is an eigenfunction for $\D_{k}$ with eigenvalue $\l$, then \cref{thm:Laplace_semi-definite_self-adjoint} implies $\l$ is real and positive. Since $\l = s(1-s)$ and $\l$ is real, $s$ and $1-s$ are either conjugates or real. In the former case, $s = 1-\conj{s}$ and we find that
    \[
      \s = 1-\s \quad \text{and} \quad t = t.
    \]
    Therefore $s = \frac{1}{2}+it$. In the later case, since $s$ is real and $\l$ is positive we must have $s \in (0,1)$. It follows that in either case, we may write $\l = \frac{1}{4}+r^{2}$ and $s = \frac{1}{2}+\nu$ for unique $r$ and $\nu$ satisfying $r \in \R$ or $ir \in \big[0,\frac{1}{2}\big)$ and $\nu \in i\R$ or $\nu \in \big[0,\frac{1}{2}\big)$ corresponding to the two cases respectively. In particular, we also have $\l = \frac{1}{4}-\nu^{2}$ and $\nu = ir$. We refer to $r$ as the \textbf{spectral parameter}\index{spectral parameter} of $f$ and $\nu$ as the \textbf{type}\index{type} of $f$. We collect the ways of expressing $\l$ below:
    \[
      \l = s(1-s) = \frac{1}{4}-\nu^{2} = \frac{1}{4}+r^{2}.
    \]
    Unfortunately the Eisenstein series $E_{k,\chi,\mf{a}}(z,s)$ are not $L^{2}$-integrable over $\mc{F}_{\G}$ and so do not belong to $\mc{L}_{k}(\G,\chi)$. To obtain integrable automorphic functions we will argument these Eisenstein series so that they have compact support. Let $\psi(y)$ be a bump function and let $\s_{\mf{a}}$ be a scaling matrix for the $\mf{a}$ cusp. We define the \textbf{(incomplete) Eisenstein series}\index{(incomplete) Eisenstein series} $E_{k,\chi,\mf{a}}(z,\psi)$ of weight $k$ and character $\chi$ on $\GH$ at the $\mf{a}$ cusp and with respect to $\psi(y)$ by
    \[
      E_{k,\chi,\mf{a}}(z,\psi) = \sum_{\g \in \G_{\mf{a}}\backslash\G}\cchi(\g)\e(\g,z)^{-k}\psi(\Im(\s_{\mf{a}}^{-1}\g z)).
    \]
    This series is locally absolutely uniformly convergent since only finitely many of the terms are nonzero. Indeed, $\s_{\mf{a}}^{-1}\G$ is a Fuchsian group because it is a subset of the modular group. So using $\s_{\mf{a}}^{-1}\G_{\mf{a}}\backslash\G = \G_{\infty}\backslash\s_{\mf{a}}^{-1}\G$ we see that $\{\s_{\mf{a}}^{-1}\g z:\g \in \G_{\mf{a}}\backslash\G\}$ is discrete. Since $\Im(z)$ is an open map it takes discrete sets to discrete sets so that $\{\Im(\s_{\mf{a}}^{-1}\g z):\g \in \G_{\mf{a}}\backslash\G\}$ is also discrete. Now $\psi(\Im(\s_{\mf{a}}^{-1}\g z))$ is nonzero if and only if $\Im(\s_{\mf{a}}^{-1}\g z) \in \mathrm{Supp}(\psi)$ and $\{\Im(\s_{\mf{a}}^{-1}\g z):\g \in \G_{\mf{a}}\backslash\G\} \cap \mathrm{Supp}(\psi)$ is finite as it is a discrete subset of a compact set (since $\psi(y)$ has compact support). Hence finitely many of the terms are nonzero. Also, $E_{k,\chi,\mf{a}}(z,\psi)$ is automorphic on $\GH$ and the automorphy is proved in exactly the same way as for the Eisenstein series $E_{k,\chi,\mf{a}}(z,s)$. Moreover, the compact support of $\psi(y)$ implies that $E_{k,\chi,\mf{a}}(z,\psi)$ is also compactly supported (since the function $\psi(\Im(\s_{\mf{a}}^{-1}\g z))$ is continuous and $\C$ is Hausdorff) and hence bounded on $\H$. As a consequence, $E_{k,\chi,\mf{a}}(z,\psi)$ is $L^{2}$-integrable and therefore belongs to $\mc{L}_{k}(\G,\chi)$. This is the advantage of these Eisenstein series. We collect this work as a theorem:

    \begin{theorem}
      For any bump function $\psi(y)$, the Eisenstein series
      \[
        E_{k,\chi,\mf{a}}(z,\psi) = \sum_{\g \in \G_{\mf{a}}\backslash\G}\cchi(\g)\e(\g,z)^{-k}\psi(\Im(\s_{\mf{a}}^{-1}\g z)),
      \]
      is an automorphic function on $\GH$ and belongs to $\mc{L}_{k}(\G,\chi)$.
    \end{theorem}
    
    Unfortunately, the Eisenstein series $E_{k,\chi,\mf{a}}(z,\psi)$ fail to be Maass forms because they are not eigenfunctions for the Laplace operator. This is because compactly supported functions cannot be real-analytic (which as we have already mentioned is implied for any eigenfunction of the Laplace operator). However, there is an important interaction between incomplete Eisenstein series and Maass cusp forms. Let $\mc{E}_{k}(\G,\chi)$ and $\mc{C}_{k}(\G,\chi)$ denote the subspaces of $\mc{A}_{k}(\G,\chi)$ generated by such forms respectively. If $\chi$ is the trivial character or if the weight $k$ is zero, we will suppress these dependences. Note that they are also subspaces of $\mc{B}_{k}(\G,\chi)$. Moreover, let $\mc{E}_{k,\nu}(\G,\chi)$, $\mc{C}_{k,\nu}(\G,\chi)$, $\mc{A}_{k,\nu}(\G,\chi)$, and $\mc{B}_{k,\nu}(\G,\chi)$ denote the corresponding subspaces of $\mc{E}_{k}(\G,\chi)$, $\mc{C}_{k}(\G,\chi)$, $\mc{A}_{k}(\G,\chi)$, and $\mc{B}_{k}(\G,\chi)$ whose type is $\nu$. For all of these spaces, if $\chi$ is the trivial character or if the weight $k$ is zero, we will suppress these dependences. As we will now show, $\mc{E}_{k}(\G,\chi)$ and $\mc{C}_{k}(\G,\chi)$ constitute all of $\mc{B}_{k}(\G,\chi)$. Indeed, let $f \in \mc{B}_{k}(\G,\chi)$ with $E_{k,\chi,\mf{a}}(\cdot,\psi) \in \mc{E}_{k}(\G,\chi)$. We compute their inner product:
    \begin{align*}
      \<f,E_{k,\chi,\mf{a}}(\cdot,\psi)\> &= \frac{1}{V_{\G}}\int_{\mc{F}_{\G}}f(z)\conj{E_{k,\chi,\mf{a}}(z,\psi)}\,d\mu \\
      &= \frac{1}{V_{\G}}\int_{\mc{F}_{\G}}\sum_{\g \in \GG}\chi(\g)\conj{\e(\s_{\mf{a}}^{-1}\g,z)^{-k}}f(z)\conj{\psi(\Im(\s_{\mf{a}}^{-1}\g z))}\,d\mu \\
      &= \frac{1}{V_{\G}}\int_{\mc{F}_{\G}}\sum_{\g \in \GG}\chi(\g)\conj{\e(\s_{\mf{a}}^{-1}\g,\g^{-1}\s_{\mf{a}}z)^{-k}}f(\g^{-1}\s_{\mf{a}}z)\conj{\psi(\Im(z))}\,d\mu && \text{$z \to \g^{-1}\s_{\mf{a}}z$} \\
      &= \frac{1}{V_{\G}}\int_{\mc{F}_{\G}}\sum_{\g \in \GG}\chi(\g)\conj{\left(\frac{\e(I,z)}{\e(\g^{-1},\s_{\mf{a}}z)}\right)^{-k}}f(\g^{-1}\s_{\mf{a}}z)\conj{\psi(\Im(z))}\,d\mu && \text{cocycle condition} \\
      &= \frac{1}{V_{\G}}\int_{\mc{F}_{\G}}\sum_{\g \in \GG}\chi(\g)\e(\g^{-1},\s_{\mf{a}}z)^{-k}f(\g^{-1}\s_{\mf{a}}z)\conj{\psi(\Im(z))}\,d\mu && \text{$\conj{\e(\g,z)} = \e(\g,z)^{-1}$} \\
      &= \frac{1}{V_{\G}}\int_{\mc{F}_{\G}}\sum_{\g \in \GG}\chi(\g^{-1})^{-1}\e(\g^{-1},\s_{\mf{a}}z)^{-k}f(\g^{-1}\s_{\mf{a}}z)\conj{\psi(\Im(z))}\,d\mu && \text{$\chi(\g) = \chi(\g^{-1})^{-1}$} \\
      &= \frac{1}{V_{\G}}\int_{\mc{F}_{\G}}f(\s_{\mf{a}}z)\sum_{\g \in \GG}\conj{\psi(\Im(z))}\,d\mu  && \text{automorphy} \\
      &= \int_{\G_{\infty}\backslash\H}f(\s_{\mf{a}}z)\conj{\psi(\Im(z))}\,d\mu && \text{unfolding} \\
      &= \int_{0}^{\infty}\int_{0}^{1}f(\s_{\mf{a}}(x+iy))\conj{\psi(y)}\,\frac{dx\,dy}{y^{2}} \\
      &= \int_{0}^{\infty}\left(\int_{0}^{1}f(\s_{\mf{a}}(x+iy))\,dx\right)\conj{\psi(y)}\,\frac{dy}{y^{2}}.
    \end{align*}
    The inner integral is precisely the constant term in the Fourier series of $f$ at the $\mf{a}$ cusp. It follows that $f$ is orthogonal to $\mc{E}_{k}(\G,\chi)$ if and only if $f$ is a cusp form. By what we have just shown,
    \[
      \mc{B}_{k}(\G,\chi) = \mc{E}_{k}(\G,\chi) \op \mc{C}_{k}(\G,\chi) \quad \text{and} \quad \mc{B}_{k,\nu}(\G,\chi) = \mc{E}_{k,\nu}(\G,\chi) \op \mc{C}_{k,\nu}(\G,\chi),
    \]
    and since $\mc{B}_{k}(\G,\chi)$ is dense in $\mc{L}_{k}(\G,\chi)$ we have
    \[
      \mc{L}_{k}(\G,\chi) = \conj{\mc{E}_{k}(\G,\chi)} \op \conj{\mc{C}_{k}(\G,\chi)},
    \]
    where the closure is with respect to the topology induced by the $L^{2}$-norm.
  \section{Spectral Theory of the Laplace Operator}
    We are now ready to discuss the spectral theory of the Laplace operator $\D_{k}$. What we want to do is to decompose $\mc{L}_{k}(\G,\chi)$ into subspaces invariant under $\D_{k}$ such that on each subspace $\D_{k}$ has either pure point spectrum, absolutely continuous spectrum, or residual spectrum. Although the proof is beyond the scope of this text, the spectral resolution of the Laplace operator on $\mc{C}_{k}(\G,\chi)$ is as follows (see \cite{iwaniec2002spectral} for a proof in the weight zero case and \cite{cohenmodular2017} for notes on the general case):

    \begin{theorem}\label{thm:cusp_form_spectrum}
      The Laplace operator $\D_{k}$ has pure point spectrum on $\mc{C}_{k}(\G,\chi)$. The corresponding subspaces $\mc{C}_{k,\nu}(\G,\chi)$ have finite dimension and are mutually orthogonal. Letting $\{u_{j}\}$ be any orthonormal basis of cusp forms for $\mc{C}_{k}(\G,\chi)$, every $f \in \mc{C}_{k}(\G,\chi)$ admits a series of the form
      \[
        f(z) = \sum_{j}\<f,u_{j}\>u_{j}(z),
      \]
      which is locally absolutely uniformly convergent if $f \in \mc{D}_{k}(\G,\chi)$ and converges in the $L^{2}$-norm otherwise.
    \end{theorem}

    We will now discuss the spectrum of the Laplace operator on $\mc{E}_{k}(\G,\chi)$. Essential is the meromorphic continuation of the Eisenstein series $E_{k,\chi,\mf{a}}(z,s)$ (see \cite{iwaniec2002spectral} for a proof in the weight zero case and \cite{cohenmodular2017} for notes on the general case):

    \begin{theorem}\label{thm:meromorphic_continuation_of_Eisenstein_series}
      Let $\mf{a}$ and $\mf{b}$ be cusps of $\GH$. The Eisenstein series $E_{k,\chi,\mf{a}}(z,s)$ admits meromorphic continuation to $\C$ in the $s$-plane, via a Fourier series at the $\mf{b}$ cusp given by
      \[
        E_{k,\chi,\mf{a}}(\s_{\mf{b}}z,s) = \d_{\mf{a},\mf{b}}y^{s}+\tau_{\mf{a},\mf{b}}(s)y^{1-s}+\sum_{n \neq 0}\tau_{\mf{a},\mf{b}}(n,s)W_{\sgn(n)\frac{k}{2},s-\frac{1}{2}}(4\pi|n|y)e^{2\pi inx},
      \]
      where $\tau_{\mf{a},\mf{b}}(s)$ and $\tau_{\mf{a},\mf{b}}(n,s)$ are meromorphic functions.
    \end{theorem}

    The Eisenstein series $E_{k,\chi,\mf{a}}(z,s)$ also satisfy a functional equation. To state it we need some notation. Fix an ordering of the cusps $\mf{a}$ of $\GH$ and define
    \[
      \mc{E}(z,s) = (E_{k,\chi,\mf{a}}(z,s))_{\mf{a}}^{t} \quad \text{and} \quad \Phi(s) = (\tau_{\mf{a},\mf{b}}(s))_{\mf{a},\mf{b}}.
    \]
    In other words, $\mc{E}(z,s)$ is the column vector of the Eisenstein series and $\Phi(s)$ is the square matrix of meromorphic functions $\tau_{\mf{a},\mf{b}}(s)$ described in \cref{thm:meromorphic_continuation_of_Eisenstein_series}. Then we have the following (see \cite{iwaniec2002spectral} for a proof in the weight zero case and \cite{cohenmodular2017} for notes on the general case): 

    \begin{theorem}\label{thm:functional_equation_of_Eisenstein_series}
      The Eisenstein series $E_{k,\chi,\mf{a}}(z,s)$ of weight $k$ and character $\chi$ on $\GH$ satisfy the functional equation 
      \[
        \mc{E}(z,s) = \Phi(s)\mc{E}(z,1-s).
      \]
      Moreover, the matrix $\Phi(s)$ satisfies the functional equation
      \[
        \Phi(s)\Phi(1-s) = I,
      \]
      is unitary on the line $\Re(s) = \frac{1}{2}$, and hermitian if $s$ is real.
    \end{theorem}

    Understanding the poles of $\tau_{\mf{a},\mf{b}}$ are also important for understanding the poles of the Eisenstein series $E_{k,\chi,\mf{a}}(z,s)$ (see \cite{iwaniec2002spectral} for a proof in the weight zero case and \cite{cohenmodular2017} for notes on the general case):

    \begin{theorem}\label{thm:residues_of_Eisenstein_series}
      The functions $\tau_{\mf{a},\mf{b}}(s)$ are meromorphic for $\Re(s) \ge \frac{1}{2}$ with a finite number of simple poles in the segment $(\frac{1}{2},1]$. A pole of $\tau_{\mf{a},\mf{b}}(s)$ is also a pole of $\tau_{\mf{a},\mf{a}}(s)$. Moreover, the poles of $E_{k,\chi,\mf{a}}(z,s)$ are among the poles of $\tau_{\mf{a},\mf{a}}(s)$, $E_{k,\chi,\mf{a}}(z,s)$ has no poles on the line $\Re(s) = \frac{1}{2}$, and the residues of $E_{k,\chi,\mf{a}}(z,s)$ are Maass forms in $\mc{E}_{k}(\G,\chi)$.
    \end{theorem}

    To begin decomposing the space $\mc{E}_{k}(\G,\chi)$, consider the subspace $C_{0}^{\infty}(\R_{> 0})$ of $\mc{L}^{2}(\R_{> 0})$ with the normalized standard inner product
    \[
      \<f,g\> = \frac{1}{2\pi}\int_{0}^{\infty}f(r)\conj{g(r)}\,dr,
    \]
    for any $f,g \in C_{0}^{\infty}(\R_{> 0})$. For each cups $\mf{a}$ of $\GH$ we associate the \textbf{Eisenstein transform}\index{Eisenstein transform} $E_{k,\chi,\mf{a}}:C_{0}^{\infty}(\R_{> 0}) \to \mc{A}_{k}(\G,\chi)$ defined by
    \[
      (E_{k,\chi,\mf{a}}f)(z) = \frac{1}{4\pi}\int_{0}^{\infty}f(r)E_{k,\chi,\mf{a}}\left(z,\frac{1}{2}+\nu\right)\,dr.
    \]
    Clearly $E_{k,\chi,\mf{a}}f$ is automorphic because $E_{k,\chi,\mf{a}}(z,s)$ is. It is not too hard to show the following (see \cite{iwaniec2002spectral} for a proof in the weight zero case and \cite{cohenmodular2017} for notes on the general case):

    \begin{proposition}\label{prop:Eisenstein_transform_property}
      If $f \in C_{0}^{\infty}(\R_{> 0})$, then $E_{\mf{a}}f$ is $L^{2}$-integrable over $\mc{F}_{\G}$. That is, $E_{k,\chi,\mf{a}}$ maps $C_{0}^{\infty}(\R_{> 0})$ into $\mc{L}_{k}(\G,\chi)$. Moreover,
      \[
        \<E_{k,\chi,\mf{a}}f,E_{k,\chi,\mf{b}}g\> = \d_{\mf{a},\mf{b}}\<f,g\>,
      \]
      for any $f,g \in C_{0}^{\infty}(\R_{> 0})$ and any two cusps $\mf{a}$ and $\mf{b}$.
    \end{proposition}

    We let $\mc{E}_{k,\mf{a}}(\G,\chi)$ denote the image of the Eisenstein transform $E_{k,\chi,\mf{a}}$. We call $\mc{E}_{k,\mf{a}}(\G,\chi)$ the \textbf{Eisenstein space}\index{Eisenstein space} of $E_{k,\chi,\mf{a}}(z,s)$. An immediate consequence of \cref{prop:Eisenstein_transform_property} is that the Eisenstein spaces for distinct cusps are orthogonal. Moreover, since $E_{k,\chi,\mf{a}}\left(z,\frac{1}{2}+\nu\right)$ is an eigenfunction for the Laplace operator with eigenvalue $\l = \frac{1}{4}+r^{2}$, and $f$ and $E_{k,\chi,\mf{a}}\left(z,\frac{1}{2}+\nu\right)$ are smooth, the Leibniz integral rule implies
    \[
      \D E_{k,\chi,\mf{a}}= E_{k,\chi,\mf{a}}M,
    \]
    where $M:C_{0}^{\infty}(\R_{> 0}) \to C_{0}^{\infty}(\R_{> 0})$ is the multiplication operator given by
    \[
      (Mf)(r) = \left(\frac{1}{4}+r^{2}\right)f(r),
    \]
    for all $f \in C_{0}^{\infty}(\R_{> 0})$. Therefore if $E_{k,\chi,\mf{a}}f$ belongs to $\mc{E}_{k,\mf{a}}(\G,\chi)$ then so does $E_{k,\chi,\mf{a}}(Mf)$. But as $f,Mf \in C_{0}^{\infty}(\R_{> 0})$, this means $\mc{E}_{k,\mf{a}}(\G,\chi)$ is invariant under the Laplace operator. While the Eisenstein spaces are invariant, they do not make up all of $\mc{E}_{k}(\G,\chi)$. By \cref{thm:residues_of_Eisenstein_series}, the residues of the Eisenstein series belong to $\mc{E}_{k}(\G,\chi)$. Let $\mc{R}_{k}(\G,\chi)$ denote the subspace generated by the residues of these Eisenstein series. We call any element of $\mc{R}_{k}(\G,\chi)$ a \textbf{(residual) Maass form}\index{(residual) Maass form} (by \cref{thm:residues_of_Eisenstein_series} they are Maass forms). Also let $\mc{R}_{k,s_{j}}(\G,\chi)$ denote the subspace generated by those residues taken at $s = s_{j}$. For both of these subspaces, if $\chi$ is the trivial character of if $k = 0$, we will suppress the dependences accordingly. Since there are finitely many cusps of $\GH$, each $\mc{R}_{k,s_{j}}(\G,\chi)$ is finite dimensional. As the number of residues in $(\frac{1}{2},1]$ is finite by \cref{thm:residues_of_Eisenstein_series}, it follows that $\mc{R}_{k}(\G,\chi)$ is finite dimensional too. So $\mc{R}_{k}(\G,\chi)$ decomposes as
    \[
      \mc{R}_{k}(\G,\chi) = \bigoplus_{\frac{1}{2} < s_{j} \le 1}\mc{R}_{k,s_{j}}(\G,\chi).
    \]
    This decomposition is orthogonal because the Maass forms belonging to distinct subspaces $\mc{R}_{k,s_{j}}(\G,\chi)$ have distinct eigenvalues and eigenfunctions of self-adjoint operators are orthogonal (recall that $\D_{k}$ is self-adjoint by \cref{thm:Laplace_semi-definite_self-adjoint}). Also, each subspace $\mc{R}_{k,s_{j}}(\G,\chi)$ is clearly invariant under the Laplace operator because its elements are Maass forms.
    We are now ready for the spectral resolution. Although the proof is beyond the scope of this text, the spectral resolution of the Laplace operator on $\mc{E}_{k}(\G,\chi)$ is as follows (see \cite{iwaniec2002spectral} for a proof in the weight zero case and \cite{cohenmodular2017} for notes on the general case):

    \begin{theorem}\label{thm:incomplete_Eisenstein_series_spectrum}
      $\mc{E}_{k}(\G,\chi)$ admits the orthogonal decomposition
      \[
        \mc{E}_{k}(\G,\chi) = \mc{R}_{k}(\G,\chi) \bigop_{\mf{a}}\mc{E}_{k}(\G,\chi),
      \]
      where the direct sum is over the cusps of $\GH$. The Laplace operator $\D_{k}$ has discrete spectrum on $\mc{R}_{k}(\G,\chi)$ in the segment $[0,\frac{1}{4})$ and has pure continuous spectrum on each Eisenstein space $\mc{E}_{k,\mf{a}}(\G,\chi)$ covering the segment $\big[\frac{1}{4},\infty\big)$ uniformly with multiplicity $1$. Letting $\{u_{j}\}$ be any orthonormal basis residual Maass forms for $\mc{R}_{k}(\G,\chi)$, every $f \in \mc{E}_{k,\mf{a}}(\G,\chi)$ admits a decomposition of the form
      \[
        f(z) = \sum_{j}\<f,u_{j}\>u_{j}(z)+\sum_{\mf{a}}\frac{1}{4\pi}\int_{-\infty}^{\infty}\left\<f,E_{k,\chi,\mf{a}}\left(\cdot,\frac{1}{2}+\nu\right)\right\>E_{k,\chi,\mf{a}}\left(z,\frac{1}{2}+\nu\right)\,dr.
      \]
      The series is locally absolutely uniformly convergent and the integrals are locally absolutely uniformly bounded if $f \in \mc{D}_{k}(\G,\chi)$ and converges in the $L^{2}$-norm otherwise.
    \end{theorem}

    Combining \cref{thm:cusp_form_spectrum,thm:incomplete_Eisenstein_series_spectrum} gives the full spectral resolution of $\mc{L}_{k}(\G,\chi)$:

    \begin{theorem}\label{thm:the_full_spectral_resolution}
      $\mc{B}_{k}(\G,\chi)$ admits the orthogonal decomposition
      \[
        \mc{B}_{k}(\G,\chi) = \mc{C}_{k}(\G,\chi) \op \mc{R}_{k}(\G,\chi) \bigop_{\mf{a}}\mc{E}_{k}(\G,\chi),
      \]
      where the sum is over all cusps of $\GH$. The Laplace operator has pure point spectrum on $\mc{C}_{k}(\G,\chi)$, discrete spectrum on $\mc{R}_{k}(\G,\chi)$, and absolutely continuous spectrum on $\mc{E}_{k}(\G,\chi)$. Letting $\{u_{j}\}$ be any orthonormal basis of Maass forms for $\mc{C}_{k}(\G,\chi) \op \mc{R}_{k}(\G,\chi)$, any $f \in \mc{L}_{k}(\G,\chi)$ has a series of the form
      \[
        f(z) = \sum_{j}\<f,u_{j}\>u_{j}(z)+\sum_{\mf{a}}\frac{1}{4\pi}\int_{-\infty}^{\infty}\left\<f,E_{k,\chi,\mf{a}}\left(\cdot,\frac{1}{2}+\nu\right)\right\>E_{k,\chi,\mf{a}}\left(z,\frac{1}{2}+\nu\right)\,dr,
      \]
      which is locally absolutely uniformly convergent if $f \in \mc{D}_{k}(\G,\chi)$ and in the $L^{2}$-norm otherwise. Moreover,
      \[
        \mc{L}_{k}(\G,\chi) = \conj{\mc{C}_{k}(\G,\chi)} \op  \conj{\mc{R}_{k}(\G,\chi)} \bigop_{\mf{a}}\conj{\mc{E}_{k}(\G,\chi)},
      \]
      where the closure is with respect to the topology induced by the $L^{2}$-norm.
    \end{theorem}
    \begin{proof}
      Combine \cref{thm:cusp_form_spectrum,thm:incomplete_Eisenstein_series_spectrum} and use the fact that $\mc{B}_{k}(\G,\chi) = \mc{E}_{k}(\G,\chi) \op \mc{C}_{k}(\G,\chi)$ for the first statement. The last statement holds because $\mc{B}_{k}(\G,\chi)$ is dense in $\mc{L}_{k}(\G,\chi)$.
    \end{proof}
  \section{Double Coset Operators}
    We can extend the theory of double coset operators to weight zero Maass form just as we did for holomorphic forms. Indeed, for any $\a \in \GL_{2}^{+}(\Q)$, we define the operator $[\a]$ on $\mc{A}_{\nu}(\G)$ to be the linear operator given by
    \[
      (f[\a])(z) = \det(\a)^{-\frac{1}{2}}f(\a z),
    \]
    Clearly $[\a]$ is multiplicative. Moreover, if $\g \in \G$ and we choose the representative with positive determinant, then the chain of equalities
    \[
      (f[\g])(z) = f(\g z) = f(z),
    \]
    is equivalent to the automorphy of $f$ on $\GH$. For any two congruence subgroups $\G_{1}$ and $\G_{2}$ (not necessarily of the same level) and any $\a \in \GL_{2}^{+}(\Q)$, we define the \textbf{double coset operator}\index{double coset operator} $[\G_{1}\a\G_{2}]$ to be the linear operator on $\mc{A}_{\nu}(\G_{1})$ given by
    \[
      (f[\G_{1}\a\G_{2}])(z) = \sum_{j}(f[\b_{j}])(z) = \sum_{j}\det(\b_{j})^{-\frac{1}{2}}f(\b_{j}z).
    \]
    As was the case for holomorphic forms, \cref{prop:double_congruence_subgroup_coset_decomposition_is_finite} implies that this sum is finite. Mimicking the same argument for $[\G_{1}\a\G_{2}]_{k}$, we see that $[\G_{1}\a\G_{2}]$ is also well-defined. There is also an analogous statement about the double coset operators for Maass forms:

    \begin{proposition}\label{prop:double_coset_operator_preserves_subspaces_Maass}
      For any two congruence subgroups $\G_{1}$ and $\G_{2}$, $[\G_{1}\a\G_{2}]$ maps $\mc{A}_{\nu}(\G_{1})$ into $\mc{A}_{\nu}(\G_{2})$. Moreover, $[\G_{1}\a\G_{2}]$ preserves the subspace of cusp forms.
    \end{proposition}
    \begin{proof}
      Mimicking the proof of \cref{prop:double_coset_operator_preserves_subspaces_holomorphic} with $k = 0$ (except $k = \frac{1}{2}$ for the power of the determinant), smoothness replacing holomorphy, and the analogous growth condition for Maass forms, the only piece left to verify is that $f[\G_{1}\a\G_{2}]$ is an eigenfunction for $\D$ with eigenvalue $\l$ if $f$ is. This is easy, since
      \[
        \D(f[\G_{1}\a\G_{2}])(z) = \sum_{j}\D(f[\b_{j}])(z) = \l\sum_{j}\det(\b_{j})^{-\frac{1}{2}}f(\b_{j}z) = \l(f[\G_{1}\a\G_{2}])(z). 
      \]
      Thus $f[\G_{1}\a\G_{2}]$ is an eigenfunction for $\D$ with eigenvalue $\l$. This completes the proof.
    \end{proof}
  \section{Diamond \& Hecke Operators}
    Extending the theory of diamond operators and Hecke operators to weight zero Maass form is fairly straightforward. To see this, we have already shown that $\G_{1}(N)$ is normal in $\G_{0}(N)$ so
    \[
      \left(f\left[\G_{1}(N)\a\G_{1}(N)\right]\right)(z) = \sum_{j}(f[\b_{j}])(z) = (f[\a])(z),
    \]
    for any $\a = \begin{psmallmatrix} \ast & \ast \\ \ast & d \end{psmallmatrix} \in \G_{0}(N)$. Therefore, for any $d$ taken modulo $N$, we define the \textbf{diamond operator} $\<d\>:\mc{A}_{\nu}(\G_{1}(N)) \to \mc{A}_{\nu}(\G_{1}(N))$ to be the linear operative given by
    \[
      (\<d\>f)(z) = (f[\a])(z),
    \]
    for any $\a = \begin{psmallmatrix} \ast & \ast \\ \ast & d \end{psmallmatrix} \in \G_{0}(N)$. As for holomorphic forms, the diamond operators are multiplicative and invertible. They also decompose $\mc{A}_{\nu}(\G_{1}(N))$ into eigenspaces. For any Dirichlet character modulo $N$, let
    \[
      \mc{A}_{\nu}(N,\chi) = \{f \in \mc{A}_{\nu}(\G_{1}(N)):\<d\>f = \chi(d)f \text{ for all } d \in (\Z/N\Z)^{\ast}\},
    \]
    be the $\chi$-eigenspace. Also let $\mc{C}_{\nu}(N,\chi)$ be the corresponding subspace of cusp forms. Then $\mc{A}_{\nu}(\G_{1}(N))$ admits a decomposition into these eigenspaces:

    \begin{proposition}\label{thm:diamond_operator_decomposition_Maass}
      We have a direct sum decomposition
      \[
        \mc{A}_{\nu}(\G_{1}(N)) = \bigop_{\chi \tmod{N}}\mc{A}_{\nu}(N,\chi).
      \]
      Moreover, this decomposition respects the subspace of cusp forms.
    \end{proposition}
    \begin{proof}
      Mimic the proof of \cref{thm:diamond_operator_decomposition_holomorphic}.
    \end{proof}

    If $\g = \begin{psmallmatrix} \ast & \ast \\ \ast & d \end{psmallmatrix} \in \G_{0}(N)$ and we choose the representative with positive determinant, then $\chi(\g) = \chi(d)$ and the chain of equalities
    \[
      (\<d\>f)(z) = (f[\g])(z) = f(\g z) = \chi(d)f(z),
    \]
    is equivalent to the automorphy of $f$ with character $\chi$ on $\G_{0}(N)\backslash\H$. So $f$ is a Maass form with character $\chi$ on $\G_{0}(N)\backslash\H$ if and only if $f[\g] = \chi(\g)f$ for all $\g \in \G_{0}(N)$ where $\g$ is chosen to be the representative with positive determinant. This means that if $\mc{A}_{\nu}(\G,\chi)$ denotes the space of Maass forms on $\GH$ of type $\nu$ and character $\chi$, and $\mc{C}_{\nu}(\G,\chi)$ denotes the corresponding subspace of cusp forms, then $\mc{A}_{\nu}(N,\chi) = \mc{A}_{\nu}(\G_{0}(N),\chi)$ and $\mc{C}_{\nu}(N,\chi) = \mc{C}_{\nu}(\G_{0}(N),\chi)$. So by \cref{thm:diamond_operator_decomposition_Maass}, we have
    \[
      \mc{A}_{\nu}(\G_{1}(N)) = \bigop_{\chi \tmod{N}}\mc{A}_{\nu}(\G_{0}(N),\chi),
    \]
    and this decomposition respects the subspace of cusp forms. As for holomorphic forms, this decomposition helps clarify why we consider Maass forms with nontrivial characters. We define the Hecke operators in the same way as for holomorphic forms. For a prime $p$, we define the $p$-th \textbf{Hecke operator}\index{Hecke operator} $T_{p}:\mc{A}_{\nu}(\G_{1}(N)) \to \mc{A}_{\nu}(\G_{1}(N))$ to be the linear operator given by
    \[
      (T_{p}f)(z) = \left(f\left[\G_{1}(N)\begin{pmatrix} 1 & 0 \\ 0 & p \end{pmatrix}\G_{1}(N)\right]\right)(z).
    \]
    By \cref{prop:double_coset_operator_preserves_subspaces_Maass}, $T_{p}$ preserves the subspaces of Maass forms and cusp forms. The diamond and Hecke operators commute:

    \begin{proposition}\label{prop:diamond_Hecke_operators_commute_Maass}
      For every $d \in (\Z/N\Z)^{\ast}$ and prime $p$, the diamond operator $\<d\>$ and the Hecke operator $T_{p}$ on $\mc{A}_{\nu}(\G_{1}(N))$ commute:
      \[
        \<d\>T_{p} = T_{p}\<d\>
      \]
    \end{proposition}
    \begin{proof}
      Mimic the proof of \cref{prop:diamond_Hecke_operators_commute_Maass}.
    \end{proof}

    Exactly as for holomorphic forms, \cref{lem:cosets_for_Hecke_operators} will give an explicit description of the Hecke operator $T_{p}$:

    \begin{proposition}\label{prop:explicit_description_of_Hecke_operators_Maass}
      Let $f \in \mc{A}_{\nu}(\G_{1}(N))$. Then the Hecke operator $T_{p}$ acts on $f$ as follows:
      \[
        (T_{p}f)(z) = \begin{cases} \displaystyle{\sum_{j \tmod{p}}}\left(f\left[\begin{pmatrix} 1 & j \\ 0 & p \end{pmatrix}\right]\right)(z)+\left(f\left[\begin{pmatrix} m & n \\ N & p \end{pmatrix}\begin{pmatrix} p & 0 \\ 0 & 1 \end{pmatrix}\right]\right)(z) & \text{if $p \nmid N$}, \\ \displaystyle{\sum_{j \tmod{p}}}\left(f\left[\begin{pmatrix} 1 & j \\ 0 & p \end{pmatrix}\right]\right)(z) & \text{if $p \mid N$}, \end{cases}
      \]
      where $m$ and $n$ are chosen such that $\det\left(\begin{psmallmatrix} m & n \\ N & p \end{psmallmatrix}\right) = 1$.
    \end{proposition}
    \begin{proof}
      Mimic the proof of \cref{prop:explicit_description_of_Hecke_operators_holomorphic}.
    \end{proof}

    We use \cref{prop:explicit_description_of_Hecke_operators_Maass} to understand how the Hecke operators act on the Fourier coefficients of Maass forms:

    \begin{proposition}\label{prop:prime_Hecke_operators_acting_on_Fourier_coefficients_Maass}
      Let $f \in \mc{A}_{\nu}(\G_{1}(N))$ Fourier coefficients $a_{n}(f)$, $a_{0}(f)$, and $b_{0}(f)$. Then for primes $p$ with $(p,N) = 1$,
      \begin{align*}
        (T_{p}f)(z) = (a_{0}(f)+\chi_{N,0}(p)a_{0}(\<p\>f))y^{\frac{1}{2}+\nu}&+(b_{0}(f)+\chi_{N,0}(p)b_{0}(\<p\>f))y^{\frac{1}{2}-\nu} \\
        &+ \sum_{n \neq 0}\left(a_{np}(f)+\chi_{N,0}(p)a_{\frac{n}{p}}(\<p\>f)\right)\sqrt{y}K_{\nu}(2\pi|n|y)e^{2\pi inx},
      \end{align*}
      is the Fourier series of $T_{p}f$ where it is understood that $a_{\frac{n}{p}}(f) = 0$ if $p \nmid n$. Moreover, if $f \in \mc{A}_{\nu}(N,\chi)$, then $T_{p}f \in \mc{A}_{\nu}(N,\chi)$ and
      \begin{align*}
        (T_{p}f)(z) = (a_{0}(f)+\chi(p)a_{0}(f))y^{\frac{1}{2}+\nu}&+(b_{0}(f)+\chi(p)b_{0}(f))y^{\frac{1}{2}-\nu} \\
        &+ \sum_{n \neq 0}\left(a_{np}(f)+\chi(p)a_{\frac{n}{p}}(f)\right)\sqrt{y}K_{\nu}(2\pi|n|y)e^{2\pi inx},
      \end{align*}
      where it is understood that $a_{\frac{n}{p}}(f) = 0$ if $p \nmid n$.
    \end{proposition}
    \begin{proof}
      Mimic the proof of \cref{prop:prime_Hecke_operators_acting_on_Fourier_coefficients_holomorphic}.
    \end{proof}

    As for holomorphic forms, the Hecke operators form a simultaneously commuting family with the diamond operators:

    \begin{proposition}\label{prop:Hecke_operators_commute_Maass}
      Let $p$ and $q$ be primes and $d,e \in (\Z/N\Z)^{\ast}$. Then the Hecke operators $T_{p}$ and $T_{q}$ and diamond operators $\<d\>$ and $\<e\>$ on $\mc{A}_{\nu}(\G_{1}(N))$ form a simultaneously commuting family:
      \[
        T_{p}T_{q} = T_{q}T_{p}, \quad \<d\>T_{p} = T_{p}\<d\>, \quad \text{and} \quad \<d\>\<e\> = \<e\>\<d\>.
      \]
    \end{proposition}
    \begin{proof}
      Mimic the proof of \cref{prop:Hecke_operators_commute_holomorphic}.
    \end{proof}

    We use \cref{prop:Hecke_operators_commute_Maass} to construct diamond operators $\<m\>$ and Hecke operators $T_{m}$ for all $m \ge 1$ exactly as for holomorphic forms. Explicitly, the \textbf{diamond operator}\index{diamond operator} $\<m\>:\mc{A}_{\nu}(\G_{1}(N)) \to \mc{A}_{\nu}(\G_{1}(N))$ is defined to be the linear operator given by
    \[
      \<m\> = \begin{cases} \<m\> \text{ with $m$ taken modulo $N$} & \text{if $(m,N) = 1$,} \\ 0 & \text{if $(m,N) > 1$.} \end{cases}
    \]
    For the Hecke operators, if $m = p_{1}^{r_{1}}p_{2}^{r_{2}} \cdots p_{k}^{r_{k}}$ is the prime decomposition of $m$, then the $m$-th \textbf{Hecke operator}\index{Hecke operator} $T_{m}:\mc{A}_{k,\nu}(\G,\chi) \to \mc{A}_{k,\nu}(\G,\chi)$ is the linear operator given by
    \[
      T_{m} = \prod_{1 \le i \le k}T_{p_{i}^{r_{i}}},
    \]
    where $T_{p^{r}}$ is defined inductively by
    \[
      T_{p^{r}} = \begin{cases} T_{p}T_{p^{r-1}}-\<p\>T_{p^{r-2}} & \text{if $p \nmid N$}, \\ T_{p}^{r} & \text{if $p \mid N$}, \end{cases}
    \]
    for all $r \ge 2$. By \cref{prop:Hecke_operators_commute_Maass}, the Hecke operators $T_{m}$ are multiplicative but not completely multiplicative in $m$ and they commute with the diamond operators $\<m\>$. Moreover, a more general formula for how the Hecke operators $T_{m}$ act on the Fourier coefficients can be derived:

    \begin{proposition}\label{prop:general_Hecke_operators_acting_on_Fourier_coefficients_Maass}
      Let $f \in \mc{A}_{\nu}(\G_{1}(N))$ with Fourier coefficients $a_{n}(f)$, $a_{0}(f)$, and $b_{0}(f)$. Then for $m \ge 1$ with $(m,N) = 1$,
      \begin{align*}
        (T_{m}f)(z) = \left(\sum_{d \mid m}a_{0}(\<d\>f)\right)y^{\frac{1}{2}+\nu}&+\left(\sum_{d \mid m}b_{0}(\<d\>f)\right)y^{\frac{1}{2}-\nu} \\
        &+ \sum_{n \neq 0}\left(\sum_{d \mid (n,m)}a_{\frac{nm}{d^{2}}}(\<d\>f)\right)\sqrt{y}K_{\nu}(2\pi|n|y)e^{2\pi inx},
      \end{align*}
      is the Fourier series of $T_{m}f$. Moreover, if $f \in \mc{A}_{\nu}(N,\chi)$, then
      \begin{align*}
        (T_{m}f)(z) = \left(\sum_{d \mid m}\chi(d)a_{0}(f)\right)y^{\frac{1}{2}+\nu}&+\left(\sum_{d \mid m}\chi(d)b_{0}(f)\right)y^{\frac{1}{2}-\nu} \\
        &+ \sum_{n \neq 0}\left(\sum_{d \mid (n,m)}\chi(d)a_{\frac{nm}{d^{2}}}(f)\right)\sqrt{y}K_{\nu}(2\pi|n|y)e^{2\pi inx}.
      \end{align*}
    \end{proposition}
    \begin{proof}
      Mimic the proof of \cref{prop:general_Hecke_operators_acting_on_Fourier_coefficients_holomorphic}.
    \end{proof}

    The diamond and Hecke operators turn out to be normal with respect to the Petersson inner product on the subspace of cusp forms. We can use \cref{lem:Petersson_normality_lemma} to compute adjoints:

    \begin{proposition}\label{prop:Petersson_adjoint_Maass}
      Let $\G$ be a congruence subgroup and let $\a \in \GL_{2}^{+}(\Q)$. Then the following are true:
      \begin{enumerate}[label=(\roman*)]
        \item If $\a^{-1}\G\a \subseteq \PSL_{2}(\Z)$, then for all $f \in \mc{C}_{k,\nu}(\G,\chi)$ and $g \in \mc{C}_{\nu}(\a^{-1}\G\a)$, we have
        \[
          \<f[\a],g\>_{\a^{-1}\G\a} = \<f,g[\a^{-1}]\>_{\G}.
        \]
        \item For all $f,g \in \mc{C}_{k,\nu}(\G,\chi)$, we have
        \[
          \<f[\G\a\G],g\> = \<f,g[\G\a^{-1}\G]\>.
        \]
      \end{enumerate}
      In particular, if $\a^{-1}\G\a = \G$ then $[\a]^{\ast} = [\a^{-1}]$ and $[\G\a\G]^{\ast} = [\G\a^{-1}\G]$. 
    \end{proposition}
    \begin{proof}
      Mimic the proof of \cref{prop:Petersson_adjoint_holomorphic}.
    \end{proof}

    We can now prove that the diamond and Hecke operators are normal:

    \begin{proposition}\label{prop:Hecke_operators_normal_Maass}
      On $\mc{C}_{\nu}(\G_{1}(N))$, the diamond operators $\<m\>$ and Hecke operators $T_{m}$ are normal with respect to the Petersson inner product for all $m \ge 1$ with $(m,N) = 1$. Moreover, their adjoints are given by
      \[
        \<m\>^{\ast} = \<\conj{m}\> \quad \text{and} \quad T_{p}^{\ast} = \<\conj{p}\>T_{p}.
      \]
    \end{proposition}
    \begin{proof}
      Mimic the proof of \cref{prop:Hecke_operators_normal_holomorphic}.
    \end{proof}

    When we are considering Maass forms on the full modular group, \cref{prop:Hecke_operators_normal_Maass} says that all of the diamond and Hecke operators are normal. Before discussing the spectral theory, we need one last operator. Define $T_{-1}:\mc{A}_{\nu}(\G_{1}(N)) \to \mc{A}_{\nu}(\G_{1}(N))$ to be the linear operator given by
    \[
      (T_{-1}f)(z) = f(-\conj{z}).
    \]
    Clearly $T_{-1}$ preserves the subspace of cusp forms. Moreover, we also have the following proposition encompassing important properties of the $T_{-1}$ operator:

    \begin{proposition}\label{prop:sign_operator_commutes_with_Hecke_and_diamond_and_is_normal}
      \phantom{ }
      \begin{enumerate}
          \item On $\mc{A}_{\nu}(\G_{1}(N))$, the operator $T_{-1}$ commutes with the diamond operators $\<m\>$ and Hecke operators $T_{n}$ for all $m,n \ge 1$.
          \item On $\mc{C}_{\nu}(\G_{1}(N))$ the operator $T_{-1}$ is normal with respect to the Petersson inner product and the adjoint is given by
          \[
            T_{-1}^{\ast} = -T_{-1}.
          \]
      \end{enumerate}
    \end{proposition}
    \begin{proof}
      To prove (i), for any matrix $\a \in \GL_{2}^{+}(\Q)$ observe that $-\conj{\a z} = \a(-\conj{z})$. Hence $T_{-1}$ commutes with the $[\a]$ operator. Since $T_{-1}$ is linear, it follows that it commutes with the double coset operators and hence the diamond operators and Hecke operators as well. For (ii), $z \to -\conj{z}$ is an automorphism of $\H$ sending $d\mu \to -d\mu$. So for any $f,g \in \mc{C}_{\nu}(\G_{1}(N))$, we have
      \begin{align*}
        \<T_{-1}f,g\> &= \frac{1}{V_{\G_{1}(N)}}\int_{\mc{F}_{\G_{1}(N)}}(T_{-1}f)(z)\conj{g(z)}\,d\mu \\
        &= \frac{1}{V_{\G_{1}(N)}}\int_{\mc{F}_{\G_{1}(N)}}f(-\conj{z})\conj{g(z)}\,d\mu \\
        &= -\frac{1}{V_{\G_{1}(N)}}\int_{\mc{F}_{\G_{1}(N)}}f(z)\conj{g(-\conj{z})}\,d\mu \\
        &= \<f,-T_{-1}g\>.
      \end{align*}
      This proves the adjoint formula $T_{-1}^{\ast} = -T_{-1}$ and normality is now clear.
    \end{proof}
    
    In the case of the modular group, \cref{prop:Hecke_operators_normal_Maass} says that all of the diamond and Hecke operators are normal. Suppose $f$ is a non-constant Maass form with Fourier coefficients $a_{n}(f)$. Let the eigenvalue of $T_{m}$ for $f$ be $\l_{f}(m)$. We say that the $\l_{f}(m)$ are the \textbf{Hecke eigenvalues}\index{Hecke eigenvalues} of $f$. Similar to the case for holomorphic forms, if $f$ is a Maass form on $\G_{1}(N)\backslash\H$ that is a simultaneous eigenfunction for the operator $T_{-1}$ and all diamond operators $\<m\>$ and Hecke operators $T_{m}$ with $(m,N) = 1$, we call $f$ an \textbf{eigenform}\index{eigenform} (necessarily $f$ is even or odd because $T_{-1}^{2}f = f$ so that the only possible eigenvalues are $\pm 1$). If the condition $(m,N) = 1$ can be dropped, so that $f$ is a simultaneous eigenfunction for all diamond and Hecke operators, then we say $f$ is a \textbf{Hecke-Maass eigenform}\index{Hecke-Maass eigenform}. In particular, on $\G_{1}(1)\backslash\H$ all eigenforms are Hecke-Maass eigenforms. As for holomorphic forms, if $f$ an eigenform \cref{prop:general_Hecke_operators_acting_on_Fourier_coefficients_Maass} implies that the first Fourier coefficient of $T_{m}f$ is $a_{m}(f)$ and so $a_{m}(f) = \l_{f}(m)a_{1}(f)$ for all $m \ge 1$ with $(m,N) = 1$. Therefore we cannot have $a_{1}(f) = 0$ and so we can normalize $f$ by dividing by $a_{1}(f)$ which guarantees that the Fourier series has constant term $1$. Then the $m$-th Fourier coefficient of $f$, when $(m,N) = 1$, is precisely the Hecke eigenvalue $\l_{f}(m)$. This normalization is called the \textbf{Hecke normalization}\index{Hecke normalization} of $f$. The \textbf{Petersson normalization}\index{Petersson normalization} of $f$ is where we normalize so that $\<f,f\> = 1$. From the spectral theorem we have an analogous corollary as for holomorphic forms:

    \begin{theorem}\label{thm:eigenforms_forms_spectral_theory_Maass}
      $\mc{C}_{\nu}(\G_{1}(N))$ admits an orthonormal basis of eigenforms.
    \end{theorem}
    \begin{proof}
      This follows from the spectral theorem along with \cref{prop:Hecke_operators_commute_Maass,prop:Hecke_operators_normal_Maass,prop:sign_operator_commutes_with_Hecke_and_diamond_and_is_normal}.
    \end{proof}

    In particular, \cref{thm:eigenforms_forms_spectral_theory_Maass} implies that the orthonormal basis in \cref{thm:cusp_form_spectrum} can be taken to be an orthonormal basis of eigenforms since it is clear that the $T_{-1}$ operator, diamond operators $\<m\>$, and Hecke operators $T_{m}$ all commute with $\D$. Also, just as in the holomorphic setting, we have \textbf{Hecke relations}\index{Hecke relations} for Maass forms:

    \begin{proposition}[Hecke relations, Maass version]
      Let $f \in \mc{C}_{\nu}(N,\chi)$ be a Hecke-Maass eigenform with Fourier coefficients $\l_{f}(n)$. Then the Fourier coefficients are multiplicative and satisfy
      \[
        \l_{f}(n)\l_{f}(m) = \sum_{d \mid (n,m)}\chi(d)\l_{f}\left(\frac{nm}{d^{2}}\right) \quad \text{and} \quad \l_{f}(nm) = \sum_{d \mid (n,m)}\mu(d)\chi(d)\l_{f}\left(\frac{n}{d}\right)\l_{f}\left(\frac{m}{d}\right),
      \]
      for all $n,m \ge 1$ with $(nm,N) = 1$.
    \end{proposition}
    \begin{proof}
      Mimic the proof of the Hecke relations for holomorphic forms.
    \end{proof}
    
    As an immediate consequence of the Hecke relations, the Hecke operators satisfy analogous relations:

    \begin{corollary}\label{cor:Hecke_relations_operator_Maass}
      For all $n,m \ge 1$ with $(nm,N) = 1$, we have
      \[
        T_{n}T_{m} = \sum_{d \mid (n,m)}\chi(d)T_{\frac{nm}{d^{2}}} \quad \text{and} \quad T_{nm} = \sum_{d \mid (n,m)}\mu(d)\chi(d)T_{\frac{n}{d}}T_{\frac{m}{d}}.
      \]
    \end{corollary}
    \begin{proof}
      Mimic the proof of \cref{cor:Hecke_relations_operator_holomorphic}.
    \end{proof}

    Just as for holomorphic forms, the identities in \cref{cor:Hecke_relations_operator_Maass} can also be established directly and the first identity can be used to show that the Hecke operators commute.
  \section{Atkin–Lehner Theory}
    There is also an Atkin–Lehner theory for weight zero Maass form. As with holomorphic forms, we will only deal with congruence subgroups of the form $\G_{1}(N)$ and cusp forms on $\G_{1}(N)\backslash\H$. The trivial way to lift Maass forms from a smaller level to a larger level is via the natural inclusion $\mc{C}_{\nu}(\G_{1}(M)) \subseteq \mc{C}_{\nu}(\G_{1}(N))$ provided $M \mid N$ which follows from $\G_{1}(N) \le \G_{1}(M)$. Alternatively, for any $d \mid \frac{N}{M}$, let $\a_{d} = \begin{psmallmatrix} d & 0 \\ 0 & 1 \end{psmallmatrix}$. If $f \in \mc{C}_{\nu}(\G_{1}(M))$, then
    \[
      (f[\a_{d}])(z) = f(\a_{d} z) = f(dz).
    \]
    Similar to holomorphic forms, $[\a_{d}]$ maps $\mc{C}_{\nu}(\G_{1}(M))$ into $\mc{C}_{\nu}(\G_{1}(N))$:
    
    \begin{proposition}\label{equ:lifting_operator_Maass}
      Let $M$ and $N$ be positive integers such that $M \mid N$. For any $d \mid \frac{N}{M}$, $[\a_{d}]$ maps $\mc{C}_{\nu}(\G_{1}(M))$ into $\mc{C}_{\nu}(\G_{1}(N))$.
    \end{proposition}
    \begin{proof}
      Mimicking the proof of \cref{equ:lifting_operator_holomorphic} with $k = 0$, smoothness replacing holomorphy, and the analogous growth condition for Maass forms, the only piece left to verify is that $f[\a_{d}]$ is an eigenfunction for $\D$ with eigenvalue $\l$ if $f$ is. This is easy, for
      \[
        \D(f[\a_{d}])(z) = (\D f)(dz) = \l f(dz) = \l(f[\a_{d}])(z).
      \]
      Therefore $f[\a_{d}]$ is an eigenfunction for $\D$ with eigenvalue $\l$. This completes the proof.
    \end{proof}

    We can now define oldforms and newforms. For each divisor $d$ of $N$, set
    \[
      i_{d}:\mc{C}_{\nu}\left(\G_{1}\left(\frac{N}{d}\right)\right)\x\mc{C}_{\nu}\left(\G_{1}\left(\frac{N}{d}\right)\right) \to \mc{C}_{\nu}(\G_{1}(N)) \qquad (f,g) \mapsto f+g[\a_{d}].
    \]
    This map is well-defined by \cref{equ:lifting_operator_Maass}. The subspace of \textbf{oldforms of level $N$}\index{oldforms of level $N$} is
    \[
      \mc{C}_{\nu}(\G_{1}(N))^{\mathrm{old}} = \bigop_{p \mid N}\Im(i_{p}),
    \]
    and the subspace of \textbf{newforms of level $N$}\index{newforms of level $N$} is
    \[
      \mc{C}_{\nu}(\G_{1}(N))^{\mathrm{new}} = \left(\mc{C}_{\nu}(\G_{1}(N))^{\mathrm{old}} \right)^{\perp},
    \]
    where the orthogonal complement is taken with respect to the Petersson inner product. The elements of such subspaces are called \textbf{oldforms}\index{oldforms} and \textbf{newforms}\index{newforms} respectively. Both subspaces are invariant under the diamond and Hecke operators (mimic the proof of \cref{prop:old/new_subspaces_are_invariant_holomorphic} given in \cite{diamond2005first}):

    \begin{proposition}\label{prop:old/new_subspaces_are_invariant_Maass}
      The spaces $\mc{C}_{\nu}(\G_{1}(N))^{\mathrm{old}}$ and $\mc{C}_{\nu}(\G_{1}(N))^{\mathrm{new}}$ are invariant under the diamond operators $\<m\>$ and Hecke operators $T_{m}$ for all $m \ge 1$.
    \end{proposition}

    As a corollary, these subspaces admit orthogonal bases of eigenforms:

    \begin{corollary}\label{cor:old/new_eigenbasis_Maass}
      $\mc{C}_{\nu}(\G_{1}(N))^{\mathrm{old}}$ and $\mc{C}_{\nu}(\G_{1}(N))^{\mathrm{new}}$ admit orthonormal bases of eigenforms.
    \end{corollary}
    \begin{proof}
      This follows immediately from \cref{thm:eigenforms_forms_spectral_theory_Maass,prop:old/new_subspaces_are_invariant_Maass}
    \end{proof}

    We can remove the condition $(m,N) = 1$ for eigenforms in a basis of $\mc{C}_{\nu}(\G_{1}(N))^{\mathrm{new}}$ so that the eigenforms are eigenfunctions for all of the diamond and Hecke operators. As for holomorphic forms, we need a preliminary result (mimic the proof of \cref{lem:the_main_lemma_for_newforms_holomorphic} as given in \cite{diamond2005first}):

    \begin{lemma}\label{lem:the_main_lemma_for_newforms_Maass}
      If $f \in \mc{C}_{\nu}(\G_{1}(N))$ with Fourier coefficients $a_{n}(f)$ and such that $a_{n}(f) = 0$ whenever $(n,N) = 1$, then
      \[
        f = \sum_{p \mid N}f_{p}[\a_{p}],
      \]
      for some $f_{p} \in \mc{C}_{\nu}\left(\G_{1}\left(\frac{N}{p}\right)\right)$.
    \end{lemma}

    As was the case for holomorphic forms, we observe from \cref{lem:the_main_lemma_for_newforms_Maass} that if $f \in \mc{C}_{\nu}(\G_{1}(N))$ is such that its $n$-th Fourier coefficients vanish when $n$ is relatively prime to the level, then $f$ must be an oldform. The main theorem about $\mc{C}_{\nu}(\G_{1}(N))^{\mathrm{new}}$ can now be proved. We say that $f$ is a \textbf{primitive Hecke-Maass eigenform}\index{primitive Hecke-Maass eigenform} if it is a nonzero Hecke normalized Hecke-Maass eigenform in $\mc{C}_{\nu}(\G_{1}(N))^{\mathrm{new}}$. We can now prove the main result about newforms:

    \begin{theorem}\label{thm:newforms_characterization_Maass}
      Let $f \in \mc{C}_{\nu}(\G_{1}(N))^{\mathrm{new}}$ be an eigenform. Then the following hold:
      \begin{enumerate}[label=(\roman*)]
        \item $f$ is a Hecke-Maass eigenform.
        \item If $\wtilde{f}$ satisfies the same conditions as $f$ and has the same eigenvalues for the Hecke operators, then $\wtilde{f} = cf$ for some nonzero constant $c$.
      \end{enumerate}
      Moreover, the primitive Hecke-Maass eigenforms in $\mc{C}_{\nu}(\G_{1}(N))^{\mathrm{new}}$ form an orthogonal basis with respect to the Petersson inner product and each such primitive Hecke-Maass eigenform $f$ lies in an eigenspace $\mc{C}_{\nu}(N,\chi)$.
    \end{theorem}
    \begin{proof}
      Mimic the proof of \cref{thm:newforms_characterization_holomorphic}.
    \end{proof}

    Statement (i) in \cref{thm:newforms_characterization_Maass} implies that primitive Hecke-Maass eigenforms satisfy the Hecke relations for all $n,m \ge 1$. Statement (ii) in \cref{thm:newforms_characterization_Maass} is referred to as the \textbf{multiplicity one theorem}\index{multiplicity one theorem} for Maass forms. So as is the case for holomorphic forms, $\mc{C}_{\nu}(\G_{1}(N))^{\mathrm{new}}$ contains one element per ``eigenvalue'' where we mean a set of eigenvalues one for each Hecke operator $T_{m}$. Since the Fourier coefficients are multiplicative, the Hecke relations imply that $f$ is actually determined by its Fourier coefficients at primes. 
    
    \begin{theorem}[Multiplicity one, Maass version]
      Let $f$ and $g$ be primitive Hecke-Maass eigenforms of the same eigenvalue and level. Denote the Hecke eigenvalues by $\l_{f}(n)$ and $\l_{g}(n)$ respectively. If $\l_{f}(p) = \l_{g}(p)$ for all primes $p$, then $f = g$.
    \end{theorem}
    \begin{proof}
      Mimic the proof of multiplicity one for holomorphic forms.
    \end{proof}

    Interestingly, unlike holomorphic forms it is unknown if the Fourier coefficients of Maass forms are real or even algebraic in general. We require one last piece of machinery. As for holomorphic forms, we have an involution on the space $\mc{C}_{\nu}(N,\chi)$. Recall the matrix
    \[
      W_{N} = \begin{pmatrix} 0 & -1 \\ N & 0 \end{pmatrix},
    \]
    with $\det(W_{N}) = N$. We define the \textbf{Atkin–Lehner involution}\index{Atkin–Lehner involution} $\w_{N}:\mc{C}_{\nu}(\G_{1}(N)) \to \mc{C}_{\nu}(\G_{1}(N))$ to be the linear operator given by
    \[
      (\w_{N}f)(z) = f\left(W_{N}z\right) = f\left(-\frac{1}{Nz}\right).
    \]
    To see that $\w_{N}$ is well-defined, first note that smoothness and the growth condition are obvious. For automorphy, recall that for $\g = \begin{psmallmatrix} a & b \\ c & d \end{psmallmatrix} \in \G_{1}(N)$, we have
    \[
      W_{N}\g = \begin{pmatrix} 0 & -1 \\ N & 0 \end{pmatrix}\begin{pmatrix} a & b \\ c & d \end{pmatrix} = \begin{pmatrix} -c & -d \\ Na & Nb \\ \end{pmatrix} = \begin{pmatrix} d & -N^{-1}c \\ -Nb & a \end{pmatrix}\begin{pmatrix} 0 & -1 \\ N & 0 \end{pmatrix} = \g'W_{N},
    \]
    with $\g' = \begin{psmallmatrix} d & -N^{-1}c \\ -Nb & a \end{psmallmatrix} \in \G_{1}(N)$. Then
    \[
      (\w_{N}f)(\g z) = f(W_{N}\g z) = f(\g'W_{N}z) = f\left(-\frac{1}{Nz}\right) = (\w_{N}f)(z).
    \]
    This verifies automorphy for $\w_{N}f$. Also, it is clear that $\w_{N}f$ is a cusp form because $f$ is. Hence $\w_{N}f$ is well-defined. Moreover, it is an involution because $\w_{N}^{2}f = f$ and so its only possible eigenvalues are $\pm 1$. The crucial fact we need is how $\w_{N}$ acts on $\mc{C}_{\nu}(N,\chi)$. To state the result, for $f \in \mc{C}_{\nu}(N,\chi)$ define
    \[
      \conj{f}(z) = \conj{f(-z)}.
    \]
    Then we have the following (mimic the proof for holomorphic forms given in \cite{cohenmodular2017}):

    \begin{proposition}\label{prop:Atkin_Lehner_conjugation_Maass}
      If $f \in \mc{C}_{\nu}(N,\chi)$ is a primitive Hecke-Maass eigenform, then
      \[
        \w_{N}f = \w_{N}(f)\conj{f},
      \]
      where $\conj{f} \in \mc{C}_{\nu}(N,\cchi)$ is a primitive Hecke-Maass eigenform and $\w_{N}(f) \in \C$ is nonzero with $|\w_{N}(f)| = 1$.
    \end{proposition}
  \section{The Ramanujan-Petersson Conjecture}
    As for the size of the Fourier coefficients of weight zero Maass form, much is currently unknown. But there is an analogous conjecture to the one for holomorphic forms. To state it, suppose $f \in \mc{C}_{\nu}(N,\chi)$ is a primitive Hecke-Maass eigenform with Fourier coefficients $\l_{f}(n)$. For each prime $p$, consider the polynomial
    \[
      1-\l_{f}(p)p^{-s}+\chi(p)p^{-2s}.
    \]
    We call this the $p$-th \textbf{Hecke polynomial}\index{Hecke polynomial} of $f$. Let $\a_{1}(p)$ and $\a_{2}(p)$ denote the roots. Then
    \[
      \a_{1}(p)+\a_{2}(p) = \l_{f}(p) \quad \text{and} \quad \a_{1}(p)\a_{2}(p) = \chi(p).
    \]
    The \textbf{Ramanujan-Petersson conjecture}\index{Ramanujan-Petersson conjecture} for Maass forms is following statement:

    \begin{conjecture}[Ramanujan-Petersson conjecture, Maass version]
      Suppose $f \in \mc{C}_{\nu}(N,\chi)$ is a primitive Hecke-Maass eigenform with Hecke eigenvalues $\l_{f}(n)$. Let $\a_{1}(p)$ and $\a_{2}(p)$ be the roots of the $p$-th Hecke polynomial. Then for all primes $p$,
      \[
        |\l_{f}(p)| \le 2.
      \]
      Moreover, if $p \nmid N$, then
      \[
        |\a_{1}(p)| = |\a_{2}(p)| = 1.
      \]
    \end{conjecture}

    The Ramanujan-Petersson conjecture has not been proven, but there has been partial progress toward the conjecture. The current best bound is $|\l_{f}(p)| \le 2p^{\frac{7}{64}}$ and is due to Kim and Sarnak (see \cite{kim2003functoriality} for the proof). Nevertheless, we can get close to the Ramanujan-Petersson conjecture without much work. Let $f \in \mc{C}_{\nu}(N,\chi)$ be a primitive Hecke-Maass eigenform. Fix some $Y > 0$ and consider
    \[
      \int_{Y}^{\infty}\int_{0}^{1}|f(x+iy)|^{2}\,\frac{dx\,dy}{y^{2}}.
    \]
    Since $f$ is a cusp form, this integral is locally absolutely uniformly bounded by \cref{prop:decay_compacta_integral}.
    Moreover, this integral can be expressed as
    \[
      \int_{Y}^{\infty}\int_{0}^{1}\sum_{n,m \neq 0}\l_{f}(n)\conj{\l_{f}(m)}K_{\nu}(2\pi|n|y)\conj{K_{\nu}(2\pi|m|y)}e^{2\pi i(n-m)x}e^{-2\pi(n+m)y}\,\frac{dx\,dy}{y}.
    \]
    Appealing to the dominated convergence theorem, we can interchange the sum and the inner integral. Then \cref{equ:Dirac_integral_representation} implies that the inner integral cuts off all of the terms except the diagonal resulting in
    \[
      \int_{Y}^{\infty}\sum_{n \neq 0}|\l_{f}(n)|^{2}|K_{\nu}(2\pi|n|y)|^{2}e^{-4\pi ny}\,\frac{dx\,dy}{y}.
    \]
    As this expression is finite, we have
    \[
      |\l_{f}(n)|^{2}\int_{Y}^{\infty}K_{\nu}(2\pi|n|y)|^{2}e^{-4\pi ny}\,\frac{dx\,dy}{y} \ll \int_{Y}^{\infty}\int_{0}^{1}|f(x+iy)|^{2}\,\frac{dx\,dy}{y^{2}},
    \]
    where we note that the integral on the left-hand side is finite. Now $f$ is bounded on $\H$ so that
    \[
      \int_{Y}^{\infty}\int_{0}^{1}|f(x+iy)|^{2}\,\frac{dx\,dy}{y^{2}} \ll \int_{Y}^{\infty}\int_{0}^{1}\frac{dx\,dy}{y^{2}} \ll \frac{1}{Y}.
    \]
    Putting these two estimates together gives
    \[
      |\l_{f}(n)|^{2}\int_{Y}^{\infty}K_{\nu}(2\pi|n|y)|^{2}e^{-4\pi ny}\,\frac{dx\,dy}{y} \ll \frac{1}{Y}.
    \]
    Taking $Y = \frac{1}{n}$ results in
    \[
      \l_{f}(n) \ll n^{\frac{1}{2}}.
    \]
    This bound is known as the \textbf{Hecke bound}\index{Hecke bound} for Maass forms. However, the Ramanujan-Petersson conjecture and the Hecke relations together give the bound $\l_{f}(n) \ll \s_{0}(n)n^{\frac{1}{2}} \ll_{\e} n^{\frac{1}{2}+\e}$. It turns out that the Ramanujan-Petersson conjecture is tightly connected to another conjecture of Selberg about the smallest possible eigenvalue of weight zero Maass form on $\GH$. Note that the possible eigenvalues are discrete by \cref{thm:the_full_spectral_resolution} and so there exists a smallest eigenvalue. To state it, recall that if $f$ is a Maass form with eigenvalue $\l$ and spectral parameter $r$ on $\GH$, then $\l = \frac{1}{4}+r^{2}$ with either $r \in \R$ or $ir \in [0,\frac{1}{2})$. The \textbf{Selberg conjecture}\index{Selberg conjecture} claims that the second case never occurs in weight zero:

    \begin{conjecture}[Selberg conjecture]
      If $\l$ is the smallest eigenvalue for weight zero Maass forms on $\GH$, then
      \[
        \l \ge \frac{1}{4}.
      \]
    \end{conjecture}

    Selberg was able to achieve a remarkable lower bound using the analytic continuation of a certain Dirichlet series and the Weil bound for Kloosterman sums (see \cite{iwaniec2002spectral} for a proof):

    \begin{theorem}
      If $\l$ is the smallest eigenvalue for weight zero Maass forms on $\GH$, then
      \[
        \l \ge \frac{3}{16}.
      \]
    \end{theorem}

    In the language of automorphic representations, these two conjectures are a consequence of a much larger conjecture (see \cite{blomer2013role} for details).
  \section{Twists of Maass Forms}
    We can also twist of Maass forms by Dirichlet characters. Let $f \in \mc{A}_{\nu}(N,\chi)$ with Fourier series
    \[
      f(z) = a_{0}(f)y^{\frac{1}{2}+\nu}+b_{0}(f)y^{\frac{1}{2}-\nu}+\sum_{n \neq 0}a_{n}(f)\sqrt{y}K_{\nu}(2\pi|n|y)e^{2\pi inx}.
    \]
    and let $\psi$ be a primitive Dirichlet character modulo $M$. We define the \textbf{twisted Maass form}\index{twisted Maass form} $f \ox \psi$ of $f$ twisted by $\psi$ by the Fourier series
    \[
      (f \ox \psi)(z) = a_{0}(f)\psi(0)y^{\frac{1}{2}+\nu}+b_{0}(f)\psi(0)y^{\frac{1}{2}-\nu}+\sum_{n \neq 0}a_{n}(f)\psi(n)\sqrt{y}K_{\nu}(2\pi|n|y)e^{2\pi inx}.
    \]
    In order for $f \ox \psi$ to be well-defined, we need to prove that it is a Maass form. The following proposition proves this and more when $\psi$ is primitive:

    \begin{proposition}\label{prop:twisted_Maass_forms_primitive}
      Suppose $f \in \mc{A}_{\nu}(N,\chi)$ and $\psi$ is a primitive Dirichlet character of conductor $q$. Then $f \ox \psi \in \mc{A}_{\nu}(Nq^{2},\chi\psi^{2})$. Moreover, if $f$ is a cusp form then so is $f \ox \psi$.
    \end{proposition}
    \begin{proof}
      Mimicking the proof of \cref{prop:twisted_holomorphic_forms} with $k = 0$, smoothness replacing holomorphy, and the analogous growth condition for Maass forms, the only piece left to verify is that $f \ox \psi$ is an eigenfunction for $\D$ with eigenvalue $\l$ if $f$ is in the case $\psi$ is primitive. This is easy, since
      \[
        \D(f \ox \chi)(z) = \frac{1}{\tau(\conj{\psi})}\sum_{r \tmod{q}}\conj{\psi}(r)\D(f)\left(z+\frac{r}{q}\right) =  \frac{\l}{\tau(\conj{\psi})}\sum_{r \tmod{q}}\conj{\psi}(r)f\left(z+\frac{r}{q}\right) = \l(f \ox \chi)(z).
      \]
    \end{proof}

    The generalization of \cref{prop:twisted_Maass_forms_primitive} to all characters is slightly more involved. Define operators $U_{p}$ and $V_{p}$ on $\mc{A}_{\nu}(\G_{1}(N))$ to be the linear operators given by
    \[
      (U_{p}f)(z) = a_{0}(f)y^{\frac{1}{2}+\nu}+b_{0}(f)y^{\frac{1}{2}-\nu}+\sum_{n \neq 0}a_{np}(f)\sqrt{y}K_{\nu}(2\pi|n|y)e^{2\pi inx},
    \]
    and
    \[
      (V_{p}f)(z) = a_{0}(f)(py)^{\frac{1}{2}+\nu}+b_{0}(f)(py)^{\frac{1}{2}-\nu}+\sum_{n \neq 0}a_{n}(f)\sqrt{py}K_{\nu}(2\pi|n|py)e^{2\pi inpx},
    \]
    if $f$ has Fourier series
    \[
      f(z) = a_{0}(f)y^{\frac{1}{2}+\nu}+b_{0}(f)y^{\frac{1}{2}-\nu}+\sum_{n \neq 0}a_{n}(f)\sqrt{y}K_{\nu}(2\pi|n|y)e^{2\pi inx}.
    \]
    We will show that both $U_{p}$ and $V_{p}$ map $\mc{A}_{\nu}(\G_{1}(N))$ into $\mc{A}_{\nu}(\G_{1}(Np))$ and more:

    \begin{lemma}\label{lem:twisted_Maass_lemma}
      For any prime $p$, $U_{p}$ and $V_{p}$ map $\mc{A}_{\nu}(\G_{1}(N))$ into $\mc{A}_{\nu}(\G_{1}(Np))$. In particular, $U_{p}$ and $V_{p}$ map $\mc{A}_{\nu}(N,\chi)$ into $\mc{A}_{\nu}(Np,\chi\chi_{p,0})$. Moreover, $U_{p}$ and $V_{p}$ preserve the subspace of cusp forms.
    \end{lemma}
    \begin{proof}
      Mimic the proof of \cref{thm:diamond_operator_decomposition_holomorphic}.
    \end{proof}

    We can now generalize \cref{prop:twisted_Maass_forms_primitive} to all characters:

    \begin{proposition}\label{prop:twisted_Maass_forms}
      Suppose $f \in \mc{A}_{\nu}(N,\chi)$ and $\psi$ is a Dirichlet character modulo $M$. Then $f \ox \psi \in \mc{A}_{\nu}(NM^{2},\chi\psi^{2})$. Moreover, if $f$ is a cusp form then so is $f \ox \psi$.
    \end{proposition}
    \begin{proof}
      Mimicking the proof of \cref{prop:twisted_holomorphic_forms}, it remains to show that $f \ox \psi_{p,0}$ is an eigenfunction with eigenvalue $\l$ if $f$ is. As $U_{p} = T_{p}$ for the $p$-th Hecke operator on $\mc{A}_{\nu}(\G_{1}(Np))$, $U_{p}$ commutes with $\D$. It is also clear that $V_{p}$ commutes with $\D$. These facts together with
      \[
        f \ox \psi_{p,0} = f-V_{p}U_{p}f,
      \]
      show that $f \ox \psi_{p,0}$ is an eigenfunction with eigenvalue $\l$ if $f$ is.
    \end{proof}