%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass{resume} % Use the custom resume.cls style

\usepackage[left=0.75in,top=0.6in,right=0.75in,bottom=0.6in]{geometry}% Document margins
\newcommand{\tab}[1]{\hspace{.2667\textwidth}\rlap{#1}}
\newcommand{\itab}[1]{\hspace{0em}\rlap{#1}}
\name{Henry Twiss} % Your name
\address{henryjtwiss@gmail.com \\ www.henrytwiss.com \\ 651.368.4884}

\pagestyle{plain} 
\pagenumbering{arabic}

\begin{document}

\begin{rSection}{Research Interests}
    \begin{center}Weyl group multiple Dirichlet series -- Half-integral weight modular forms -- Siegel zeros\end{center}
\end{rSection}

\begin{rSection}{Education}
    {\bf Brown University}, Providence, RI \hfill {2021-Present} \\
    PhD Mathematics, \textit{expected May 2026} \\
    \hphantom{\quad}Advisor: Jeff Hoffstein

    {\bf University of Minnesota}, Minneapolis, MN \hfill {May 2021} \\
    B.S. Mathematics, \textit{summa cum laude} \\
    \hphantom{\quad}Advisor: Adrian Diaconu
\end{rSection}

\begin{rSection}{Publications and Preprints}
    \begin{enumerate}
        \item {A. Diaconu, H. Twiss. Secondary terms in the asymptotics of moments of $L$-functions. Preprint,
        2020; arXiv:2008.13297. \textit{JNT Prime}.}
        \item {S. Creech, H. Twiss. An extension of Venkatesh's converse theorem to half-integral weight forms in the Selberg class. \textit{Preprint}.}
        \item {K. Benli, S. Goel, H. Twiss, A. Zaman. Explicit zero-repulsion of Dirichlet $L$-functions. \textit{In preparation}.}
        \item {H. Twiss. Subconvexity for $\mathrm{GL}(2)$ $L$-functions via multiple Dirichlet series. \textit{In preparation}.}
        \item {H. Twiss. Simultaneous non-vanishing for prodcuts of elliptic $L$-functions. \textit{In preparation}.}
    \end{enumerate}
\end{rSection}

\begin{rSection}{Awards, Scholarships, Fellowships, and Grants}
    DOMESTIC \\
    {$\bullet$ Brown Mathematics First Year Fellowship, Brown University} \hfill {2021} \\
    {$\bullet$ NSF Graduate Research Fellowship, National} \hfill {2021} \\
    {$\bullet$ Barry M. Goldwater Scholarship, National} \hfill {2020} \\
    {$\bullet$ Hans H. Dalaker Scholarship, University of Minnesota} \hfill {2020} \\
    {$\bullet$ William H. Burgum Scholarship, University of Minnesota} \hfill {2019} \\
    {$\bullet$ Honors, every semester at University of Minnesota} \hfill {2017-2021} \\
    {$\bullet$ Dean's List, every semester at University of Minnesota} \hfill {2017-2021}

    TRAVEL GRANTS \\
    {$\bullet$ BIRS Travel Grant, Inclusive Paths in Explicit Number Theory} \hfill {2023} \\
    {$\bullet$ University of Chicago RTG Travel Grant, Notre Dame Topology \& Geometry Workshop} \hfill {2019} 
\end{rSection}

\begin{rSection}{Experience}
    RESEARCH \\
    {\bf DRS The Nonabelian Delta-symbol Method Research Group}, Durham, NC \\
    \hphantom{\quad} Analytic Number Theory and Automorphic Forms \hfill {Dec. 2023 - Feb. 2024} \\
    {\bf BIRS Inclusive Paths in Explicit Number Theory Summer School}, Kelowna, CA \\
    \hphantom{\quad} Explicit Analytic Number Theory \hfill {Jul. 2023 - Jul. 2023} \\
    {\bf University of Minnesota REU}, Minneapolis, MN \\
    \hphantom{\quad} Algebra, Combinatorics, and Representation Theory \hfill {Jun. 2020 - Aug. 2020}

    TEACHING \\
    {\bf Brown University}, Providence, RI \\
    \hphantom{\quad} Lecturer, Analytic Number Theory II \hfill {Mar. 2024 - May 2024} \\
    {\bf Art of Problem Solving}, Online \\
    \hphantom{\quad} TA, Introduction to Algebra B \hfill {May 2018 - Aug. 2018} \\
    \hphantom{\quad} TA, Introduction to Algebra A \hfill {May 2018 - Aug. 2018} \\
\end{rSection}

\begin{rSection}{Workshops and Conferences}
    {AMS New England Graduate Student Conference} \hfill {2022} \\
    \hphantom{\quad}Spring Graduate Student Conference, Providence, RI \\
    {Online Conference in Automorphic Forms} \hfill {2020} \\
    \hphantom{\quad}Summer Conference in Automorphic Forms, Online \\
    {Algebraic Combinatorics Workshop} \hfill {2020} \\
    \hphantom{\quad}Spring Workshop in Algebraic Combinatorics, Online \\
    {Notre Dame RTG Topology \& Geometry Workshop} \hfill {2019} \\
    \hphantom{\quad}Summer Workshop in Topology and Geometry, Notre Dame, IN
\end{rSection}

\begin{rSection}{Seminars}
    {\bf Analytic Number Theory Learning Seminar}, Brown University \hfill {2023-Present} \\
    {\bf Graduate Student Seminar}, Brown University \hfill {2021-Present} \\
    {\bf Algebra and Number Theory Seminar}, Brown University \hfill {2021-Present} \\
    {\bf Student Combinatorics and Algebra Seminar}, University of Minnesota \hfill {2020-2021} \\
    {\bf Student Number Theory Seminar}, University of Minnesota \hfill {2019-2021} \\
    {\bf Undergraduate Mathematics Research Seminar}, University of Minnesota \hfill {2017-2021} \\
    {\bf Summer Student Representation Theory Seminar}, University of Minnesota \hfill {2019-2020} \\
\end{rSection}

\begin{rSection}{Presentations and Posters}
    RESEARCH TALKS \\
    {Subconvexity for $\mathrm{GL}(2)$ $L$-functions in the conductor aspect.} \hfill {Oct. 2024} \\
    \hphantom{\quad}PIMS CRG: $L$-functions in Analytic Number Theory \\
    {Simultaneous non-vanishing for products of elliptic $L$-functions.} \hfill {Sep. 2024} \\
    \hphantom{\quad}Brown University \\
    {\em Explicit zero-repulsion of Dirichlet L-functions.} \hfill {Nov. 2023} \\
    \hphantom{\quad}Brown University \\
    {\em A converse theorem in half-integral weight.} \hfill {May 2023} \\
    \hphantom{\quad}Brown University \\
    {\em Root systems attached to moments of quadratic Dirichlet L-functions.} \hfill {May 2021} \\
    \hphantom{\quad}University of Minnesota \\

    EXPOSITORY TALKS \\
    {\em Statistics of L-functions modeled by random matrix theory.} \hfill {Mar. 2023} \\ 
    \hphantom{\quad}Brown University \\
    {\em A synopsis of the origin story of WMDS.} \hfill {Apr. 2022} \\
    \hphantom{\quad}Brown University \\
    {\em An introduction to Weyl group multiple Dirichlet series.} \hfill {Apr. 2022} \\
    \hphantom{\quad}Brown University \\
    {\em $k$-Schur functions.} \hfill {Jul. 2020} \\ 
    \hphantom{\quad}University of Minnesota \\
\end{rSection}

\begin{rSection}{Outreach}
    {\bf Organizer}, AMS New England Graduate Student Conference, Brown University \hfill {2024} \\
    {\bf Mentor}, Directed Reading Program, Brown University \hfill {2020-2022} \\
    {\bf Organizer}, Undergraduate Mathematics Research Seminar, University of Minnesota \hfill {2020 - 2021} \\
    {\bf Panelist}, Mathematics Project Minnesota, University of Minnesota \hfill {2020} \\
    {\bf Panelist}, Mathematics Major Exploration Event, University of Minnesota \hfill {2020}
\end{rSection}

\begin{rSection}{Skills}
    \begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex}} l }
        Programming Languages \ & Python, C++ \\
        Computer Algebra Systems \ & SageMath, Mathematica \\
        Typeset \ & LaTeX, Tikz, Beamer \\
    \end{tabular}
\end{rSection}

\end{document}